### 2019-04-20 paper/main.tex
setup git with overleaf

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage[backend=biber,sorting=none]{biblatex}
\usepackage[margin=1.25in]{geometry}
\addbibresource{mybib.tex}

\title{Dynamical Neural Network Models\\for Sequence Learning}
\author{Sharath Ramkumar\\
Advisor: Dr. Robert Kozma\\University of Massachusetts Amherst\\COMPSCI 496: Independent Study}
\date{}

\begin{document}
\maketitle

\begin{abstract}
In this study, we explore various neural network models for learning sequences. We also compare the robustness of these network models to randomized temporal noise and propose alternative spiking neural architectures.
\end{abstract}

\section*{Introduction}

Neural network models are able to achieve superhuman performance on static tasks through recent break through in deep learning. However, the majority of real-world time-series data is often complex and noisy. As a result, we need dynamic models that can adapt to changing data streams to learn and predict in an robust, unsupervised fashion.

\section*{Background}
There have been some recent studies comparing various models for time-series prediction tasks \cite{cui2016continuous} on discretized data. In this study, we sill replicate their results to establish a baseline and propose unsupervised spiking neural architectures for performing this task. Spiking neurons \cite{gerstner2002spiking} are biologically-inspired models of neurons. Spiking neural networks (SNNs) \cite{maass1997networks} are organized connections between these spiking neurons which have more energy efficient \cite{cruz2012energy} implementations on neuromorphic hardware.

\section*{Methodology}

\subsection*{Artificial Dataset}

Cui et al. (2016) propose an artificial dataset of sequences (formed with characters) with overlapping subsequences. A sequence is sampled from the dataset and presented to the model at each time step. After the last character of the sequence is presented, a character is sampled from the noise distribution and shown to the model. This process is repeated until $10,000$ characters (counting both sequences and noise characters) are shown to the model. After the model sees $10,000$ characters, the last character of sequences with shared subsequences is swapped. The performance on this task is the accuracy of predicting the last character over a window of the last $100$ sequences. A sample dataset is summarized in Table \ref{tab:dataset}.

\begin{table}[!h]
    \centering
    \begin{tabular}{|c|c|} \hline
        Pre-$10,000$ & Post-$10,000$  \\ \hline
        \begin{tabular}{|c|c|c|}
            Start & Subsequence & End \\ \hline
            $6$ & $8, 7, 4, 2, 3$ & $0$ \\ \hline
            $1$ & $8, 7, 4, 2, 3$ & $5$ \\ \hline
            $6$ & $3, 4, 2, 7, 8$ & $5$ \\ \hline
            $1$ & $3, 4, 2, 7, 8$ & $0$ \\ \hline
            $0$ & $9, 7, 8, 5, 3, 4$ & $1$ \\ \hline
            $2$ & $9, 7, 8, 5, 3, 4$ & $6$ \\ \hline
            $0$ & $4, 3, 5, 8, 7, 9$ & $6$ \\ \hline
            $2$ & $4, 3, 5, 8, 7, 9$ & $1$ \\ \hline
        \end{tabular} &  \begin{tabular}{|c|c|c|}
            Start & Subsequence & End \\ \hline
            $6$ & $8, 7, 4, 2, 3$ & $5$ \\ \hline
            $1$ & $8, 7, 4, 2, 3$ & $0$ \\ \hline
            $6$ & $3, 4, 2, 7, 8$ & $0$ \\ \hline
            $1$ & $3, 4, 2, 7, 8$ & $5$ \\ \hline
            $0$ & $9, 7, 8, 5, 3, 4$ & $6$ \\ \hline
            $2$ & $9, 7, 8, 5, 3, 4$ & $1$ \\ \hline
            $0$ & $4, 3, 5, 8, 7, 9$ & $1$ \\ \hline
            $2$ & $4, 3, 5, 8, 7, 9$ & $6$ \\ \hline
        \end{tabular}\\ \hline
    \end{tabular}
    \caption{A sample artificial dataset for this task. The ending character can be predicted by learning the start character and the first character of the shared subsequence.}
    \label{tab:dataset}
\end{table}

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.7\linewidth]{matrix-distances.png}
    \caption{Heatmap of squared errors between distributed random encodings for the sequence characters, with $-1$ as the separating bit for ease of visualization.}
    \label{fig:encoding-distance}
\end{figure}

\subsection*{Input Encoding}

To present each of these discrete categories to the model, we have to encode the categories to a vector representations. One possibility is one-hot encoding where the vector is the same size the number of unique characters in the sequence, but this representation scales poorly when the number of unique characters increases. For this reason, the characters are encoded as random vectors with real values in the interval $\left[-1, 1\right]$, similar to distributed representations used in natural language learning. \cite{mikolov2013distributed} The euclidean distances between pairs of unique sequence characters using a $25$ length random ending is shown in Figure \ref{fig:encoding-distance}. The decoder for converting vectors back to character uses a nearest neighbor approach, therefore the precision in the output vector from the model is important as the number of noise characters increases. Another possibility to consider for the input encoding would be the sparse distributed categorical encoder utilized by Cui et al. (2016) for their hierarchical temporal memory (HTM) model.

\section*{Models}

\subsection*{Long short-term memory networks (LSTM)}

Long short-term memory \cite{hochreiter1997long} networks are able to achieve state of the art results on various sequence learning tasks, so they are a good starting point to establish baseline performance on this task. We use the same LSTM architecture proposed by Cui et al. (2016) with $25$ input neurons connected to a hidden layer of $20$ LSTM cells and $25$ output neurons. The network is trained using backpropagation through time (BPTT) \cite{mozer1995focused} on the last $1000$ seen elements. The output is classified using the nearest neighbor decoder.

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.75\linewidth]{lstm.png}
    \caption{The network architecture for the LSTM-online model. The LSTM cells maintain an internal hidden state.}
    \label{fig:lstm-online-model}
\end{figure}

\subsection*{Time-delay neural networks (TDNN)}

Time-delay neural networks (TDNN) are feed-forward neural networks trained using a lag on a window of previous data. \cite{waibel1995phoneme} For this task, the TDNN is trained on the last $1000$ characters using a lag of $10$ using backpropagation. \cite{rojas1996backpropagation} Again, using the model proposed by Cui et al. (2016), the first layer has $250$ input neurons that are fully connected to a hidden layer of $200$ neurons. The hidden layers utilize a sigmoid non-linearity and are then fully connected to $25$ output neurons. As with the LSTM model, the output is classified using the nearest neighbor decoder.

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.75\linewidth]{tdnn.png}
    \caption{The network architecture for the TDNN/TDSNN model.}
    \label{fig:lstm-online-model}
\end{figure}

\subsection*{Time-delay spiking neural network (TDSNN)}

A common approach to training spiking neural networks \cite{diehl2015fast} is through the transfer of weights learned through backpropagation on an identical non-spiking neural network and then scaling the weights. Using this approach, we can convert the TDNN model trained with a bias on the output layer (due to the lack of negative spikes) to an equivalent spiking network using the approach developed by Diehl et al. (2016)

\subsubsection*{Readout}

The drawback of using this method when we need to approximate real-values is the loss of precision based on the duration of the input. For this task, we show the input for $500$ simulated milliseconds. The summed spikes from the output layer are converted to the $25$ length vector by dividing by the runtime and subtracting $1$. As with the other models, the output is classified using the nearest neighbor decoder.

%\subsection*{K-Nearest Neighbor (KNN)}

\subsection*{Columnar Spiking Neural Network (CSNN)}

We propose a spiking neural network architecture, with $10$ inputs, each fully connected to $1$ of $10$ columns of $100$ spiking neurons. Each of the columns has a Hebbian connection to each of the other columns. To map the spikes from this network, we train a  K-Nearest Neighbor model using previous spikes and values. \cite{beliaev2007time} The model diagram is shown in Figure \ref{fig:csnn-network-diagram}.

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.7\linewidth]{csnn.png}
    \caption{The network architecture for the CSNN model.}
    \label{fig:csnn-network-diagram}
\end{figure}

\section*{Experiments}

\subsection*{Prediction Accuracy}

We tested each of the models (LSTM, TDNN, TDSNN, CSNN) on the discrete sequence learning task. The prediction accuracy results are shown in Figure \ref{fig:prediction-accuracy}. The prediction accuracy is the percent of correct predictions over a window of the last $100$ sequences.

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.9\linewidth]{prediction-accuracy.png}
    \caption{Each of the models were tested on their ability to predict the last element of the sequence.}
    \label{fig:prediction-accuracy}
\end{figure}

The CSNN prediction accuracy dramatically drops after the sequence endings are swapped. To improve performance, we can use a window for the data samples in the KNN Classifier. Furthermore, the learning rates for the Hebbian updates could be more carefully chosen.

%\subsection*{Perturbation}

%Another important property of each of these models is the robustness to temporal noise. We introduce an $\alpha$ parameters which represents the probability that a character is swapped for another character.

%\subsection*{Continuous Dataset}

%\section*{Conclusion}

\newpage
\printbibliography[title={References}]
\end{document}

### 2019-04-20 paper/mybib.tex
setup git with overleaf

@article{cui2016continuous,
  title={Continuous online sequence learning with an unsupervised neural network model},
  author={Cui, Yuwei and Ahmad, Subutai and Hawkins, Jeff},
  journal={Neural computation},
  volume={28},
  number={11},
  pages={2474--2504},
  year={2016},
  publisher={MIT Press}
}

@article{waibel1995phoneme,
  title={Phoneme recognition using time-delay neural networks},
  author={Waibel, Alexander and Hanazawa, Toshiyuki and Hinton, Geoffrey and Shikano, Kiyohiro and Lang, Kevin J},
  journal={Backpropagation: Theory, Architectures and Applications},
  pages={35--61},
  year={1995},
  publisher={Lawrence Erlbaum Assoc. Mahwah, NJ}
}

@article{diehl2015unsupervised,
  title={Unsupervised learning of digit recognition using spike-timing-dependent plasticity},
  author={Diehl, Peter U and Cook, Matthew},
  journal={Frontiers in computational neuroscience},
  volume={9},
  pages={99},
  year={2015},
  publisher={Frontiers}
}

@book{gerstner2002spiking,
  title={Spiking neuron models: Single neurons, populations, plasticity},
  author={Gerstner, Wulfram and Kistler, Werner M},
  year={2002},
  publisher={Cambridge university press}
}

@article{cruz2012energy,
  title={Energy-efficient neuron, synapse and STDP integrated circuits},
  author={Cruz-Albrecht, Jose M and Yung, Michael W and Srinivasa, Narayan},
  journal={IEEE transactions on biomedical circuits and systems},
  volume={6},
  number={3},
  pages={246--256},
  year={2012},
  publisher={IEEE}
}

@article{maass1997networks,
  title={Networks of spiking neurons: the third generation of neural network models},
  author={Maass, Wolfgang},
  journal={Neural networks},
  volume={10},
  number={9},
  pages={1659--1671},
  year={1997},
  publisher={Elsevier}
}

@inproceedings{mikolov2013distributed,
  title={Distributed representations of words and phrases and their compositionality},
  author={Mikolov, Tomas and Sutskever, Ilya and Chen, Kai and Corrado, Greg S and Dean, Jeff},
  booktitle={Advances in neural information processing systems},
  pages={3111--3119},
  year={2013}
}

@article{hochreiter1997long,
  title={Long short-term memory},
  author={Hochreiter, Sepp and Schmidhuber, J{\"u}rgen},
  journal={Neural computation},
  volume={9},
  number={8},
  pages={1735--1780},
  year={1997},
  publisher={MIT Press}
}

@article{mozer1995focused,
  title={A focused backpropagation algorithm for temporal},
  author={Mozer, Michael C},
  journal={Backpropagation: Theory, architectures, and applications},
  volume={137},
  year={1995}
}

@incollection{rojas1996backpropagation,
  title={The backpropagation algorithm},
  author={Rojas, Raul},
  booktitle={Neural networks},
  pages={149--182},
  year={1996},
  publisher={Springer}
}

@inproceedings{diehl2015fast,
  title={Fast-classifying, high-accuracy spiking deep networks through weight and threshold balancing},
  author={Diehl, Peter U and Neil, Daniel and Binas, Jonathan and Cook, Matthew and Liu, Shih-Chii and Pfeiffer, Michael},
  booktitle={2015 International Joint Conference on Neural Networks (IJCNN)},
  pages={1--8},
  year={2015},
  organization={IEEE}
}

@article{beliaev2007time,
  title={Time series prediction using chaotic neural networks on the CATS benchmark},
  author={Beliaev, Igor and Kozma, Robert},
  journal={Neurocomputing},
  volume={70},
  number={13-15},
  pages={2426--2439},
  year={2007},
  publisher={Elsevier}
}

### 2019-04-21 experiments/td/run.sh
combined td scripts

@@ -1,2 +1,7 @@
 #!/bin/sh
-pipenv run python tdsnn.py $1
+
+if [ "$2" == true ]; then
+    pipenv run python td.py --noise_level $1 --no_negative
+else
+    pipenv run python td.py --noise_level $1
+fi

### 2019-04-21 experiments/td/run2.sh

@@ -1,2 +1,0 @@
-#!/bin/sh
-pipenv run python tdnsnn.py

### 2019-04-21 experiments/td/submit.sh

@@ -1,29 +1,5 @@
-sbatch -p 1080ti-long --gres=gpu:1 run2.sh
-sbatch -p 1080ti-long --gres=gpu:1 run2.sh
-sbatch -p 1080ti-long --gres=gpu:1 run2.sh
-sbatch -p 1080ti-long --gres=gpu:1 run2.sh
-sbatch -p 1080ti-long --gres=gpu:1 run2.sh
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0.00
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0.00
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0.00
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0.00
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0.00
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0.01
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0.02
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0.03
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0.04
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0.05
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0.06
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0.07
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0.08
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0.09
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0.10
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0.12
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0.13
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0.14
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0.15
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0.16
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0.17
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0.18
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0.19
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0.20
[…]

### 2019-04-21 experiments/td/td.py

@@ -1,0 +1,184 @@
+from argparse import ArgumentParser
+import pickle
+import numpy as np
+import torch
+import torch.nn as nn
+import torch.optim as optim
+from bindsnet.conversion import SubtractiveResetIFNodes, ann_to_snn
+from bindsnet.network.monitors import Monitor
+
+
+args = None
+
+
+class TDNN(nn.Module):
+    def __init__(self):
+        super(TDNN, self).__init__()
+        self.fc1 = nn.Linear(10*25, 200)
+        self.fc2 = nn.Linear(200, 25)
+
+    def forward(self, x):
+        x = torch.relu(self.fc1(x))
+        x = self.fc2(x)
+        return x
+
+
+class Encoder():
+    def __init__(self):
+        self.encodings = {}
+
+    def encode(self, x):
+        if x in self.encodings:
+            return self.encodings[x]
+        self.encodings[x] = torch.rand(25)*2 - 1
+        return self.encodings[x]
+
+    def decode(self, v):
+        nearest = None
+        best = float('inf')
+        for x, e in self.encodings.items():
+            dist = (torch.sum((v - e).pow(2))).pow(0.5)
+            if dist < best:
+                best = dist
+                nearest = x
+        return nearest
+
+    def precode(self, stream):
+        for i in stream:
+            self.encode(i)
+
+
+def add_noise(stream):
+    ret = list(stream)
+    subs = [0, 1, 2, 3, 4, 5, 6, 7, 8, 9]
+    for i in range(len(ret)):
+        u = torch.rand(1)*100
+        if u < args.noise_level:
+            ret[i] = subs[int(torch.randint(0, len(subs), (1, )))]
+    return ret
+
+
+def moving_average(a, n=100):
+    moving_average = []
+    for i in range(len(a)):
+        start = max(0, i - n)
+        values = a[start:i+1]
+        moving_average.append(np.sum(values) / float(len(values)))
+    return np.array(moving_average)
+
+
+def convert(ann, dataset):
+    snn = ann_to_snn(ann, input_shape=(1, 10*25), data=dataset)
+    if not args.no_negative:
+        nr = SubtractiveResetIFNodes(
+            50, [50], False, refrac=0, reset=0, thresh=1)
+        nr.dt = 1.0
+        nr.network = snn
+        snn.layers['2'] = nr
[…]

### 2019-04-21 experiments/td/tdnn.py

@@ -1,100 +1,0 @@
-import sys
-import pickle
-import torch
-import torch.nn as nn
-import torch.optim as optim
-
-seed = 0
-noise_level = float(sys.argv[1]) if len(sys.argv) > 1 else 0
-torch.manual_seed(seed)
-try: 
-    torch.set_default_tensor_type('torch.cuda.FloatTensor')
-except:
-    pass
-
-class TDNN(nn.Module):
-    def __init__(self):
-        super(TDNN, self).__init__()
-        self.fc1 = nn.Linear(10*25, 200)
-        self.fc2 = nn.Linear(200, 25)
-
-    def forward(self, x):
-        x = torch.sigmoid(self.fc1(x))
-        x = torch.sigmoid(self.fc2(x))
-        return x 
-
-class Encoder():
-    def __init__(self):
-        self.encodings = {}
-
-    def encode(self, x):
-        if x in self.encodings:
-            return self.encodings[x]
-        self.encodings[x] = torch.rand(25)*2 - 1
-        return self.encodings[x]
-
-    def decode(self, v):
-        nearest = None
-        best = float('inf')
-        for x, e in self.encodings.items():
-            dist = (torch.sum((v - e).pow(2))).pow(0.5)
-            if dist < best:
-                best = dist
-                nearest = x
-        return nearest
-    
-    def precode(self, stream):
-        for i in stream:
-            self.encode(i)
-
-def add_noise(stream):
-    ret = list(stream)
-    subs = [0, 1, 2, 3, 4, 5, 6, 7, 8, 9]
-    for i in range(len(ret)):
-        u = torch.rand(1)
-        if u < noise_level:
-            ret[i] = subs[int(torch.randint(0, len(subs), (1, )))]
-    return ret
-
-tdnn = TDNN()
-criterion = nn.MSELoss()
-optimizer = optim.SGD(tdnn.parameters(), lr=0.01)
-original_stream = pickle.load(open('dataset.pkl', 'rb'))['noisy']
-encoder = Encoder()
-encoder.precode([0, 1, 2, 3, 4, 5, 6, 7, 8, 9])
-stream = add_noise(original_stream)
-
-print('it,target,tdnn_prediction,noise_level,training_loss')
-for it in range(11, 20000):
-    training_loss = 0
-    if it > 1000:
-        for epoch in range(1):
-            for i in range(max(0, it-1000), it-11):
-                x = stream[i:i+10]
-                y = stream[i+10]
-            
[…]

### 2019-04-21 experiments/td/tdnsnn.py

@@ -1,134 +1,0 @@
-import sys
-import pickle
-import torch
-import torch.nn as nn
-import torch.optim as optim
-from bindsnet.conversion import SubtractiveResetIFNodes, ann_to_snn
-from bindsnet.network.monitors import Monitor
-from copy import deepcopy
-
-seed = 0
-noise_level = float(sys.argv[1]) if len(sys.argv) > 1 else 0
-torch.manual_seed(seed)
-try: 
-    torch.set_default_tensor_type('torch.cuda.FloatTensor')
-except:
-    pass
-
-class TDNN(nn.Module):
-    def __init__(self):
-        super(TDNN, self).__init__()
-        self.fc1 = nn.Linear(10*25, 200)
-        self.fc2 = nn.Linear(200, 25)
-
-    def forward(self, x):
-        x = torch.sigmoid(self.fc1(x))
-        x = self.fc2(x)
-        return x 
-
-class Encoder():
-    def __init__(self):
-        self.encodings = {}
-
-    def encode(self, x):
-        if x in self.encodings:
-            return self.encodings[x]
-        self.encodings[x] = torch.rand(25)*2 - 1
-        return self.encodings[x]
-
-    def decode(self, v):
-        nearest = None
-        best = float('inf')
-        for x, e in self.encodings.items():
-            dist = (torch.sum((v - e).pow(2))).pow(0.5)
-            if dist < best:
-                best = dist
-                nearest = x
-        return nearest
-    
-    def precode(self, stream):
-        for i in stream:
-            self.encode(i)
-
-def add_noise(stream):
-    ret = list(stream)
-    subs = [0, 1, 2, 3, 4, 5, 6, 7, 8, 9]
-    for i in range(len(ret)):
-        u = torch.rand(1)
-        if u < noise_level:
-            ret[i] = subs[int(torch.randint(0, len(subs), (1, )))]
-    return ret
-
-tdnn = TDNN()
-criterion = nn.MSELoss()
-optimizer = optim.SGD(tdnn.parameters(), lr=0.01)
-original_stream = pickle.load(open('dataset.pkl', 'rb'))['noisy']
-encoder = Encoder()
-encoder.precode([0, 1, 2, 3, 4, 5, 6, 7, 8, 9])
-stream = add_noise(original_stream)
-
-runtime = 500
[…]

### 2019-04-21 experiments/td/tdsnn.py

@@ -1,119 +1,0 @@
-import sys
-import pickle
-import torch
-import torch.nn as nn
-import torch.optim as optim
-from bindsnet.conversion import ann_to_snn
-from bindsnet.network.monitors import Monitor
-
-seed = 0
-noise_level = float(sys.argv[1]) if len(sys.argv) > 1 else 0
-torch.manual_seed(seed)
-try: 
-    torch.set_default_tensor_type('torch.cuda.FloatTensor')
-except:
-    pass
-
-class TDNN(nn.Module):
-    def __init__(self):
-        super(TDNN, self).__init__()
-        self.fc1 = nn.Linear(10*25, 200)
-        self.fc2 = nn.Linear(200, 25)
-
-    def forward(self, x):
-        x = torch.sigmoid(self.fc1(x))
-        x = torch.sigmoid(self.fc2(x))
-        return x 
-
-class Encoder():
-    def __init__(self):
-        self.encodings = {}
-
-    def encode(self, x):
-        if x in self.encodings:
-            return self.encodings[x]
-        self.encodings[x] = torch.rand(25)*2 - 1
-        return self.encodings[x]
-
-    def decode(self, v):
-        nearest = None
-        best = float('inf')
-        for x, e in self.encodings.items():
-            dist = (torch.sum((v - e).pow(2))).pow(0.5)
-            if dist < best:
-                best = dist
-                nearest = x
-        return nearest
-    
-    def precode(self, stream):
-        for i in stream:
-            self.encode(i)
-
-def add_noise(stream):
-    ret = list(stream)
-    subs = [0, 1, 2, 3, 4, 5, 6, 7, 8, 9]
-    for i in range(len(ret)):
-        u = torch.rand(1)
-        if u < noise_level:
-            ret[i] = subs[int(torch.randint(0, len(subs), (1, )))]
-    return ret
-
-tdnn = TDNN()
-criterion = nn.MSELoss()
-optimizer = optim.SGD(tdnn.parameters(), lr=0.01)
-original_stream = pickle.load(open('dataset.pkl', 'rb'))['noisy']
-encoder = Encoder()
-encoder.precode([0, 1, 2, 3, 4, 5, 6, 7, 8, 9])
-stream = add_noise(original_stream)
-
-runtime = 500
-print('it,target,tdnn_prediction,tdsnn_prediction,noise_level,training_loss,tdnn_loss,tdsnn_loss,conversion_loss')
[…]

### 2019-04-21 experiments/td/td.py
flush after print;

@@ -1,4 +1,5 @@
 from argparse import ArgumentParser
+import sys
 import pickle
 import numpy as np
 import torch
@@ -161,6 +162,7 @@ def main(args):
             tdsnn_moving = np.mean(tdsnn_accuracy[max(0, len(tdsnn_accuracy) - 101):len(tdsnn_accuracy)])
 
             print(f'{it},{tdnn_moving},{tdsnn_moving},{tdnn_loss},{tdsnn_loss},{conversion_loss}')
+            sys.stdout.flush()
 
 
 if __name__ == '__main__':

### 2019-04-21 experiments/lstm/clean.sh
experimental pytorch lstm implementation

@@ -1,1 +1,0 @@
-rm *.log *.enc *.pyc

### 2019-04-21 experiments/lstm/kill.sh

@@ -1,1 +1,0 @@
-pkill -f 'python -W ignore lstm-online.py'

### 2019-04-21 experiments/lstm/lstm-1000.py

@@ -1,87 +1,0 @@
-import sys
-import numpy as np
-from collections import deque
-from pybrain.tools.shortcuts import buildNetwork
-from pybrain.structure.modules import LSTMLayer
-from pybrain.supervised import RPropMinusTrainer
-from pybrain.datasets import SequentialDataSet
-from util import *
-
-#dataset = generate(6) + generate(7)
-
-dataset_a = [[6, 8, 7, 4, 2, 3, 0],
-             [1, 8, 7, 4, 2, 3, 5],
-             [6, 3, 4, 2, 7, 8, 5],
-             [1, 3, 4, 2, 7, 8, 0],
-             [0, 9, 7, 8, 5, 3, 4, 1],
-             [2, 9, 7, 8, 5, 3, 4, 6],
-             [0, 4, 3, 5, 8, 7, 9, 6],
-             [2, 4, 3, 5, 8, 7, 9, 1]]
-
-dataset_b = [[6, 8, 7, 4, 2, 3, 5],
-             [1, 8, 7, 4, 2, 3, 0],
-             [6, 3, 4, 2, 7, 8, 0],
-             [1, 3, 4, 2, 7, 8, 5],
-             [0, 9, 7, 8, 5, 3, 4, 6],
-             [2, 9, 7, 8, 5, 3, 4, 1],
-             [0, 4, 3, 5, 8, 7, 9, 1],
-             [2, 4, 3, 5, 8, 7, 9, 6]]
-
-def refresh(seq, tar, it):
-    dataset = dataset_a if it < 10000 else dataset_b
-    chosen = np.random.choice(dataset) + [noise()]
-    target = chosen[1:] + [-1] + [-1]
-    seq.extend(chosen)
-    tar.extend(target)
-
-def window(data):
-    start = max(0, len(data) - 1000)
-    return data[start:]
-
-net = buildNetwork(25, 20, 25, hiddenclass=LSTMLayer,
-                   bias=True, outputbias=False, recurrent=True)
-
-history = []
-
-sequence = deque()
-target = deque()
-compute_counter = 0
-refresh(sequence, target, 0)
-start_logging()
-print 'it,current,target,prediction,correct'
-for it in range(0, 20000):
-    curs = sequence.popleft()
-    tars = target.popleft()
-    history.append(curs)
-
-    if len(sequence) == 0:
-        refresh(sequence, target, it)
-
-    if it > 0 and it % 1000 == 0: # this isn't needed for LSTM-1000
[…]

### 2019-04-21 experiments/lstm/lstm-online.py

@@ -1,83 +1,0 @@
-import sys
-import numpy as np
-from collections import deque
-from pybrain.tools.shortcuts import buildNetwork
-from pybrain.structure.modules import LSTMLayer
-from pybrain.supervised import BackpropTrainer
-from pybrain.datasets import SequentialDataSet
-from util import *
-
-dataset_a = [[6, 8, 7, 4, 2, 3, 0],
-             [1, 8, 7, 4, 2, 3, 5],
-             [6, 3, 4, 2, 7, 8, 5],
-             [1, 3, 4, 2, 7, 8, 0],
-             [0, 9, 7, 8, 5, 3, 4, 1],
-             [2, 9, 7, 8, 5, 3, 4, 6],
-             [0, 4, 3, 5, 8, 7, 9, 6],
-             [2, 4, 3, 5, 8, 7, 9, 1]]
-
-dataset_b = [[6, 8, 7, 4, 2, 3, 5],
-             [1, 8, 7, 4, 2, 3, 0],
-             [6, 3, 4, 2, 7, 8, 0],
-             [1, 3, 4, 2, 7, 8, 5],
-             [0, 9, 7, 8, 5, 3, 4, 6],
-             [2, 9, 7, 8, 5, 3, 4, 1],
-             [0, 4, 3, 5, 8, 7, 9, 1],
-             [2, 4, 3, 5, 8, 7, 9, 6]]
-
-def refresh(seq, tar, it):
-    dataset = dataset_a if it < 10000 else dataset_b
-    chosen = np.random.choice(dataset)
-    target = chosen[1:] + [-1] + [-1]
-    seq.extend(chosen + [noise(it)])
-    tar.extend(target)
-
-def window(data):
-    start = max(0, len(data) - 100)
-    return data[start:]
-
-net = buildNetwork(25, 20, 25, hiddenclass=LSTMLayer,
-                   bias=True, outputbias=False, recurrent=True)
-trainer = BackpropTrainer(net, dataset=SequentialDataSet(25, 25), learningrate=0.01, momentum=0)
-reset_encoder(100)
-
-history = []
-sequence = []
-target = []
-
-refresh(sequence, target, 0)
-
-start_logging()
-print 'it,current,target,prediction,correct'
-
-for it in range(1, 20000):
-    curs = sequence.pop(0)
-    tars = target.pop(0)
-    history.append(curs)
-
-    if len(sequence) == 0:
-        refresh(sequence, target, it)
-        
[…]

### 2019-04-21 experiments/lstm/lstm.py

@@ -1,0 +1,139 @@
+from argparse import ArgumentParser
+import sys
+import pickle
+import numpy as np
+import torch
+import torch.nn as nn
+import torch.optim as optim
+
+
+args = None
+
+
+class LSTMOnline(nn.Module):
+    def __init__(self):
+        super(LSTMOnline, self).__init__()
+        self.fc1 = nn.Linear(25, 20)
+        self.lstm = nn.LSTM(20, 20)
+        self.fc2 = nn.Linear(20, 25)
+        self.hidden = (torch.zeros(1, 1, 20), torch.zeros(1, 1, 20))
+
+    def forward(self, x):
+        x = self.fc1(x)
+        x, self.hidden = self.lstm(x.view(1, 1, -1), self.hidden)
+        x = self.fc2(x)
+        return x
+
+
+class Encoder():
+    def __init__(self):
+        self.encodings = {}
+
+    def encode(self, x):
+        if x in self.encodings:
+            return self.encodings[x]
+        self.encodings[x] = torch.rand(25)*2 - 1
+        return self.encodings[x]
+
+    def decode(self, v):
+        nearest = None
+        best = float('inf')
+        for x, e in self.encodings.items():
+            dist = (torch.sum((v - e).pow(2))).pow(0.5)
+            if dist < best:
+                best = dist
+                nearest = x
+        return nearest
+
+    def precode(self, stream):
+        for i in stream:
+            self.encode(i)
+
+
+def add_noise(stream):
+    ret = list(stream)
+    subs = [0, 1, 2, 3, 4, 5, 6, 7, 8, 9]
+    for i in range(len(ret)):
+        u = torch.rand(1)*100
+        if u < args.noise_level:
+            ret[i] = subs[int(torch.randint(0, len(subs), (1, )))]
+    return ret
+
+
+def moving_average(a, n=100):
+    moving_average = []
+    for i in range(len(a)):
+        start = max(0, i - n)
+        values = a[start:i+1]
+        moving_average.append(np.sum(values) / float(len(values)))
+    return np.array(moving_average)
+
+
+def main(args):
+    lstm = LSTMOnline()
+    criterion = nn.MSELoss()
+    optimizer = optim.SGD(lstm.parameters(), lr=0.01)
+    original_stream = pickle.load(open('dataset.pkl', 'rb'))['clean' if args.clean else 'noisy']
+
+    encoder = Encoder()
+    encoder.precode([0, 1, 2, 3, 4, 5, 6, 7, 8, 9])
[…]

### 2019-04-21 experiments/lstm/run.sh

@@ -1,34 +1,2 @@
-source ../venv/bin/activate
-python -W ignore lstm-online.py &
-sleep 2
-python -W ignore lstm-online.py &
-sleep 2
-python -W ignore lstm-online.py &
-sleep 2
-python -W ignore lstm-online.py &
-sleep 2
-python -W ignore lstm-online.py &
-sleep 2
-python -W ignore lstm-online.py &
-sleep 2
-python -W ignore lstm-online.py &
-sleep 2
-python -W ignore lstm-online.py &
-sleep 2
-python -W ignore lstm-online.py &
-sleep 2
-python -W ignore lstm-online.py &
-sleep 2
-python -W ignore lstm-online.py &
-sleep 2
-python -W ignore lstm-online.py &
-sleep 2
-python -W ignore lstm-online.py &
-sleep 2
-python -W ignore lstm-online.py &
-sleep 2
-python -W ignore lstm-online.py &
-sleep 2
-python -W ignore lstm-online.py &
-sleep 2
-python -W ignore lstm-online.py &
+#!/bin/sh
+pipenv run python lstm.py --noise_level $1

### 2019-04-21 experiments/lstm/submit.sh

@@ -1,0 +1,5 @@
+for ((i = 1; i <= 30; i++))
+do
+    sbatch -p 1080ti-long --gres=gpu:1 run.sh $i
+    sbatch -p 1080ti-long --gres=gpu:1 run.sh $i
+done

### 2019-04-21 experiments/lstm/util.py

@@ -1,98 +1,0 @@
-import numpy as np
-import random
-from time import time
-import sys
-import pickle
-
-__start = str(int(time()))
-
-class __LogPrint(object):
-    def __init__(self, *files):
-        self.files = files
-    def write(self, obj):
-        for f in self.files:
-            f.write(obj)    
-    def flush(self):
-        for f in self.files:
-            f.flush()
-
-def start_logging():
-    f = open(__start + '.log', 'w')
-    sys.stdout = __LogPrint(sys.stdout, f)
-
-__settings = {
-    'encoding_size': 25,
-    'encoding_lower': -1,
-    'encoding_upper': 1,
-    'max_order': 0,
-}
-
-def generate(order, seed=42):
-    global __settings
-    __settings['max_order'] = max(order, __settings['max_order'])
-
-    random.seed(seed)
-    symbols = list(range(order + 3))
-    random.shuffle(symbols)
-    sequences = []
-    for i in range(2):
-        start = order + i - 1
-        sequences.append([symbols[start]] + symbols[:order-1] + [symbols[-1]])
-        sequences.append([symbols[start]] + symbols[:order-1][::-1] + [symbols[-2]])
-    return sequences
-
-
-def MAPE(groundTruth, prediction):
-    return np.nanmean(np.abs(groundTruth - prediction)) / np.nanmean(np.abs(groundTruth))
-
-__encodings = None
-__seed = None
-
-def reset_encoder(seed=0):
-    global __seed
-    __seed = seed
-    np.random.seed(seed)
-    global __encodings
-    __encodings = {}
-
-def save_encodings():
-    global __encodings
-    with open(__start + '.enc', 'wb') as f:
-        pickle.dump(__encodings, f)
-
-def read_encodings(fname):
-    global __encodings
-    with open(fname, 'rb') as f:
-        __encodings = pickle.load(f)
-
-def encode(symbol):
-    global __encodings, __settings
-    if symbol not in __encodings:
-        __encodings[symbol] = np.random.uniform(
-            __settings['encoding_lower'],
-            __settings['encoding_upper'],
-            __settings['encoding_size'])
-    return __encodings[symbol]
-
-def decode(vector):
-    global __encodings
-    mind = float('inf')
-    mink = None
-    for k, v in __encodings.items():
-        dist = np.sqrt(np.sum(np.square(v - vector)))
-        if dist < mind:
-            mind = dist
-            mink = k
[…]

### 2019-04-21 experiments/td/td.py

@@ -113,7 +113,7 @@ def main(args):
     tdnn_accuracy = []
     tdsnn_accuracy = []
 
-    print('it,tdnn_accuracy,tdsnn_prediction,tdnn_loss,tdsnn_loss,conversion_loss')
+    print('it,tdnn_accuracy,tdsnn_accuracy,tdnn_loss,tdsnn_loss,conversion_loss')
     for it in range(11, 20000):
         dataset = torch.zeros((989, 250))
 

### 2019-04-21 experiments/lstm/lstm.py
reset lstm hidden state before training

@@ -82,6 +82,7 @@ def main(args):
     lstm_accuracy = []
     print('it,lstm_accuracy,lstm_loss')
     for it in range(11, 20000):
+        lstm.hidden = (torch.zeros(1, 1, 20), torch.zeros(1, 1, 20))
         for i in range(max(0, it-1000), it-1):
             x = stream[i]
             y = stream[i+1]

### 2019-04-23 experiments/lstm/submit.sh
Update submit.sh

@@ -1,4 +1,4 @@
-for ((i = 1; i <= 30; i++))
+for ((i = 0; i <= 30; i++))
 do
     sbatch -p 1080ti-long --gres=gpu:1 run.sh $i
     sbatch -p 1080ti-long --gres=gpu:1 run.sh $i

### 2019-05-02 experiments/csnn/csnn.py
update the code to search for learning rate

@@ -96,7 +96,7 @@ class Prototype(Network):
         for i in range(lag):
             for j in range(lag):
                 w = torch.zeros(self.n_neurons, self.n_neurons)
-                self.add_connection(Connection(source=self.layers[f'column_{i+1}'], target=self.layers[f'column_{j+1}'], w=w, update_rule=Hebbian, nu=[args.nu1, args.nu2]), source=f'column_{i+1}', target=f'column_{j+1}')
+                self.add_connection(Connection(source=self.layers[f'column_{i+1}'], target=self.layers[f'column_{j+1}'], w=w, update_rule=Hebbian, nu=args.nu), source=f'column_{i+1}', target=f'column_{j+1}')
 
     def run(self, inpts, **kwargs) -> None:
         inpts = {k: self.encoder.encode(v).repeat(
@@ -136,13 +136,12 @@ def main():
 if __name__ == '__main__':
     parser = ArgumentParser()
     parser.add_argument('--e_size', type=int, default=25)
-    parser.add_argument('--n_neurons', type=int, default=100)
+    parser.add_argument('--n_neurons', type=int, default=500)
     parser.add_argument('--lag', type=int, default=10)
     parser.add_argument('--runtime', type=int, default=250)
     parser.add_argument('--seed', type=int, default=None)
     parser.add_argument('--noise_level', type=int, default=0)
-    parser.add_argument('--nu1', type=float, default=0)
-    parser.add_argument('--nu2', type=float, default=0)
+    parser.add_argument('--nu', type=float, default=0)
     parser.add_argument('--clean', action='store_true', default=False)
     parser.add_argument('--learning', action='store_true', default=False)
     args = parser.parse_args()

### 2019-05-02 experiments/csnn/run.sh

@@ -1,2 +1,2 @@
 #!/bin/sh
-pipenv run python csnn.py
+pipenv run python csnn.py --seed $1 --learning --nu $2

### 2019-05-02 experiments/csnn/submit.sh

@@ -1,20 +1,20 @@
-sbatch -p 1080ti-long --gres=gpu:1 run.sh
-sbatch -p 1080ti-long --gres=gpu:1 run.sh
-sbatch -p 1080ti-long --gres=gpu:1 run.sh
-sbatch -p 1080ti-long --gres=gpu:1 run.sh
-sbatch -p 1080ti-long --gres=gpu:1 run.sh
-sbatch -p 1080ti-long --gres=gpu:1 run.sh
-sbatch -p 1080ti-long --gres=gpu:1 run.sh
-sbatch -p 1080ti-long --gres=gpu:1 run.sh
-sbatch -p 1080ti-long --gres=gpu:1 run.sh
-sbatch -p 1080ti-long --gres=gpu:1 run.sh
-sbatch -p 1080ti-long --gres=gpu:1 run.sh
-sbatch -p 1080ti-long --gres=gpu:1 run.sh
-sbatch -p 1080ti-long --gres=gpu:1 run.sh
-sbatch -p 1080ti-long --gres=gpu:1 run.sh
-sbatch -p 1080ti-long --gres=gpu:1 run.sh
-sbatch -p 1080ti-long --gres=gpu:1 run.sh
-sbatch -p 1080ti-long --gres=gpu:1 run.sh
-sbatch -p 1080ti-long --gres=gpu:1 run.sh
-sbatch -p 1080ti-long --gres=gpu:1 run.sh
-sbatch -p 1080ti-long --gres=gpu:1 run.sh
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 0 0
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 1 0
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 0 0.1
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 1 0.1
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 0 0.01
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 1 0.01
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 0 0.001
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 1 0.001
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 0 0.0001
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 1 0.0001
[…]

### 2019-05-02 experiments/csnn/csnn.py
gg

@@ -136,9 +136,9 @@ def main():
 if __name__ == '__main__':
     parser = ArgumentParser()
     parser.add_argument('--e_size', type=int, default=25)
-    parser.add_argument('--n_neurons', type=int, default=500)
+    parser.add_argument('--n_neurons', type=int, default=100)
     parser.add_argument('--lag', type=int, default=10)
-    parser.add_argument('--runtime', type=int, default=250)
+    parser.add_argument('--runtime', type=int, default=500)
     parser.add_argument('--seed', type=int, default=None)
     parser.add_argument('--noise_level', type=int, default=0)
     parser.add_argument('--nu', type=float, default=0)

### 2019-05-03 experiments/csnn/csnn.py
Update csnn.py
minor fixes

@@ -114,7 +114,7 @@ def main():
     correct = []
 
     print('it,target,csnn_prediction,accuracy')
-    for cur in range(10, len(stream)):
+    for cur in range(10, len(stream)-1):
         inpt = {f'input_{i+1}': stream[cur+i-10] for i in range(args.lag)}
         target = stream[cur]
         net.reset_()
@@ -138,7 +138,7 @@ if __name__ == '__main__':
     parser.add_argument('--e_size', type=int, default=25)
     parser.add_argument('--n_neurons', type=int, default=100)
     parser.add_argument('--lag', type=int, default=10)
-    parser.add_argument('--runtime', type=int, default=500)
+    parser.add_argument('--runtime', type=int, default=100)
     parser.add_argument('--seed', type=int, default=None)
     parser.add_argument('--noise_level', type=int, default=0)
     parser.add_argument('--nu', type=float, default=0)

### 2019-05-03 experiments/csnn/submit.sh
increase search space

@@ -1,5 +1,7 @@
 sbatch -p 1080ti-long --gres=gpu:1 run.sh 0 0
 sbatch -p 1080ti-long --gres=gpu:1 run.sh 1 0
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 0 1
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 0 1
 sbatch -p 1080ti-long --gres=gpu:1 run.sh 0 0.1
 sbatch -p 1080ti-long --gres=gpu:1 run.sh 1 0.1
 sbatch -p 1080ti-long --gres=gpu:1 run.sh 0 0.01

### 2019-05-04 experiments/csnn/submit.sh
Update submit.sh

@@ -1,22 +1,10 @@
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0 0
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 1 0
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0 1
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0 1
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0 0.1
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 1 0.1
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0 0.01
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 1 0.01
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0 0.001
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 1 0.001
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0 0.0001
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 1 0.0001
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0 0.00001
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 1 0.00001
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0 0.000001
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 1 0.000001
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0 0.0000001
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 1 0.0000001
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0 0.00000001
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 1 0.00000001
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 0 0.000000001
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 1 0.000000001
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 10 0.00001
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 11 0.00001
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 12 0.00001
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 13 0.00001
[…]

### 2019-05-05 experiments/csnn/csnn.py
fixes to lstm script

@@ -14,12 +14,12 @@ args = None
 
 
 def moving_average(a, n=100):
-    moving_average = []
+    moving = []
     for i in range(len(a)):
         start = max(0, i - n)
         values = a[start:i+1]
-        moving_average.append(np.sum(values) / float(len(values)))
-    return np.array(moving_average)
+        moving.append(np.sum(values) / float(len(values)))
+    return np.array(moving)
 
 
 class Encoder():

### 2019-05-05 experiments/lstm/lstm.py

@@ -1,38 +1,46 @@
 from argparse import ArgumentParser
 import sys
 import pickle
-import numpy as np
 import torch
 import torch.nn as nn
 import torch.optim as optim
-
+import numpy as np
 
 args = None
+
+
+def moving_average(a, n=100):
+    moving = []
+    for i in range(len(a)):
+        start = max(0, i - n)
+        values = a[start:i + 1]
+        moving.append(np.sum(values) / float(len(values)))
+    return np.array(moving)
 
 
 class LSTMOnline(nn.Module):
     def __init__(self):
         super(LSTMOnline, self).__init__()
-        self.fc1 = nn.Linear(25, 20)
-        self.lstm = nn.LSTM(20, 20)
-        self.fc2 = nn.Linear(20, 25)
-        self.hidden = (torch.zeros(1, 1, 20), torch.zeros(1, 1, 20))
+        self.inpt = nn.Linear(args.e_size, args.h_size)
+        self.lstm = nn.LSTM(args.h_size, args.h_size)
+        self.out = nn.Linear(args.h_size, args.e_size)
 
-    def forward(self, x):
-        x = self.fc1(x)
-        x, self.hidden = self.lstm(x.view(1, 1, -1), self.hidden)
-        x = self.fc2(x)
-        return x
+    def forward(self, x, h=None):
+        x = self.inpt(x.view(1, -1)).unsqueeze(1)
+        x, h = self.lstm(x, h)
+        x = self.out(x.squeeze(1))
+        return x, h
 
 
 class Encoder():
-    def __init__(self):
+    def __init__(self, e_size=25):
         self.encodings = {}
+        self.e_size = e_size
 
     def encode(self, x):
         if x in self.encodings:
             return self.encodings[x]
-        self.encodings[x] = torch.rand(25)*2 - 1
+        self.encodings[x] = 2 * torch.rand(self.e_size) - 1
         return self.encodings[x]
 
     def decode(self, v):
@@ -54,87 +62,79 @@ def add_noise(stream):
     ret = list(stream)
     subs = [0, 1, 2, 3, 4, 5, 6, 7, 8, 9]
     for i in range(len(ret)):
-        u = torch.rand(1)*100
+        u = torch.rand(1) * 100
         if u < args.noise_level:
-            ret[i] = subs[int(torch.randint(0, len(subs), (1, )))]
+            ret[i] = subs[int(torch.randint(0, len(subs), (1,)))]
     return ret
 
 
[…]

### 2019-05-05 experiments/lstm/run.sh
gypsum scripts for lstm in pytorch

@@ -1,2 +1,2 @@
 #!/bin/sh
-pipenv run python lstm.py --noise_level $1
+pipenv run python lstm.py --seed $1

### 2019-05-05 experiments/lstm/submit.sh

@@ -1,5 +1,10 @@
-for ((i = 0; i <= 30; i++))
-do
-    sbatch -p 1080ti-long --gres=gpu:1 run.sh $i
-    sbatch -p 1080ti-long --gres=gpu:1 run.sh $i
-done
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 0
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 1
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 2
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 3
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 4
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 5
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 6
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 7
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 8
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 9

### 2019-05-05 experiments/csnn/csnn.py
prepared scripts and made experiment encoding pseudorandomization equal for all experiments

@@ -22,7 +22,7 @@ def moving_average(a, n=100):
     return np.array(moving)
 
 
-class Encoder():
+class Encoder:
     def __init__(self, e_size=25):
         self.encodings = {}
         self.e_size = e_size
@@ -30,7 +30,7 @@ class Encoder():
     def encode(self, x):
         if x in self.encodings:
             return self.encodings[x]
-        self.encodings[x] = torch.rand(self.e_size)
+        self.encodings[x] = 2 * torch.rand(self.e_size) - 1
         return self.encodings[x]
 
     def decode(self, v):
@@ -104,10 +104,21 @@ class Prototype(Network):
         super().run(inpts, self.time, **kwargs)
 
 
+def add_noise(stream):
+    ret = list(stream)
+    subs = [0, 1, 2, 3, 4, 5, 6, 7, 8, 9]
+    for i in range(len(ret)):
+        u = torch.rand(1) * 100
+        if u < args.noise_level:
+            ret[i] = subs[int(torch.randint(0, len(subs), (1,)))]
+    return ret
+
+
 def main():
-    stream = pickle.load(open('dataset.pkl', 'rb'))['clean' if args.clean else 'noisy']
-    encoder = Encoder(args.e_size)
+    original_stream = pickle.load(open('dataset.pkl', 'rb'))['clean' if args.clean else 'noisy']
+    encoder = Encoder(e_size=args.e_size)
     encoder.precode([0, 1, 2, 3, 4, 5, 6, 7, 8, 9])
+    stream = add_noise(original_stream)
 
     net = Prototype(encoder, lag=args.lag, time=args.runtime, n_neurons=args.n_neurons, learning=args.learning)
     classifier = KNNClassifier()
@@ -116,7 +127,7 @@ def main():
     print('it,target,csnn_prediction,accuracy')
     for cur in range(10, len(stream)-1):
         inpt = {f'input_{i+1}': stream[cur+i-10] for i in range(args.lag)}
-        target = stream[cur]
+        target = original_stream[cur]
         net.reset_()
         net.run(inpt)
     
@@ -151,7 +162,7 @@ if __name__ == '__main__':
         torch.manual_seed(args.seed)
     try:
         torch.set_default_tensor_type('torch.cuda.FloatTensor')
-    except:
+    except AssertionError:
         pass
 
     main()

### 2019-05-05 experiments/csnn/run.sh

@@ -1,2 +1,2 @@
 #!/bin/sh
-pipenv run python csnn.py --seed $1 --learning --nu $2
+pipenv run python csnn.py --seed $1 --learning --nu 0.00001

### 2019-05-05 experiments/csnn/submit.sh

@@ -1,10 +1,10 @@
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 10 0.00001
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 11 0.00001
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 12 0.00001
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 13 0.00001
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 14 0.00001
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 15 0.00001
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 16 0.00001
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 17 0.00001
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 18 0.00001
-sbatch -p 1080ti-long --gres=gpu:1 run.sh 19 0.00001
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 0
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 1
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 2
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 3
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 4
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 5
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 6
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 7
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 8
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 9

### 2019-05-05 experiments/lstm/lstm.py

@@ -32,7 +32,7 @@ class LSTMOnline(nn.Module):
         return x, h
 
 
-class Encoder():
+class Encoder:
     def __init__(self, e_size=25):
         self.encodings = {}
         self.e_size = e_size

### 2019-05-05 experiments/td/run.sh

@@ -1,7 +1,2 @@
 #!/bin/sh
-
-if [ "$2" == true ]; then
-    pipenv run python td.py --noise_level $1 --no_negative
-else
-    pipenv run python td.py --noise_level $1
-fi
+pipenv run python td.py --seed $1 --no_negative

### 2019-05-05 experiments/td/run_negative.sh

@@ -1,0 +1,2 @@
+#!/bin/sh
+pipenv run python td.py --seed $1

### 2019-05-05 experiments/td/submit.sh

@@ -1,5 +1,20 @@
-for ((i = 0; i <= 30; i++))
-do
-    sbatch -p 1080ti-long --gres=gpu:1 run.sh $i
-    sbatch -p 1080ti-long --gres=gpu:1 run.sh $i
-done
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 0
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 1
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 2
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 3
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 4
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 5
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 6
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 7
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 8
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 9
+sbatch -p 1080ti-long --gres=gpu:1 run_negative.sh 0
+sbatch -p 1080ti-long --gres=gpu:1 run_negative.sh 1
+sbatch -p 1080ti-long --gres=gpu:1 run_negative.sh 2
+sbatch -p 1080ti-long --gres=gpu:1 run_negative.sh 3
+sbatch -p 1080ti-long --gres=gpu:1 run_negative.sh 4
+sbatch -p 1080ti-long --gres=gpu:1 run_negative.sh 5
+sbatch -p 1080ti-long --gres=gpu:1 run_negative.sh 6
+sbatch -p 1080ti-long --gres=gpu:1 run_negative.sh 7
+sbatch -p 1080ti-long --gres=gpu:1 run_negative.sh 8
+sbatch -p 1080ti-long --gres=gpu:1 run_negative.sh 9

### 2019-05-05 experiments/td/td.py

@@ -24,14 +24,15 @@ class TDNN(nn.Module):
         return x
 
 
-class Encoder():
-    def __init__(self):
+class Encoder:
+    def __init__(self, e_size=25):
         self.encodings = {}
+        self.e_size = e_size
 
     def encode(self, x):
         if x in self.encodings:
             return self.encodings[x]
-        self.encodings[x] = torch.rand(25)*2 - 1
+        self.encodings[x] = 2 * torch.rand(self.e_size) - 1
         return self.encodings[x]
 
     def decode(self, v):
@@ -60,12 +61,12 @@ def add_noise(stream):
 
 
 def moving_average(a, n=100):
-    moving_average = []
+    moving = []
     for i in range(len(a)):
         start = max(0, i - n)
         values = a[start:i+1]
-        moving_average.append(np.sum(values) / float(len(values)))
-    return np.array(moving_average)
+        moving.append(np.sum(values) / float(len(values)))
+    return np.array(moving)
 
 
 def convert(ann, dataset):
@@ -100,15 +101,15 @@ def snn_output(snn):
     return tdsnn_output
 
 
-def main(args):
-    tdnn = TDNN()
-    criterion = nn.MSELoss()
-    optimizer = optim.SGD(tdnn.parameters(), lr=0.01)
+def main():
     original_stream = pickle.load(open('dataset.pkl', 'rb'))['clean' if args.clean else 'noisy']
-
     encoder = Encoder()
     encoder.precode([0, 1, 2, 3, 4, 5, 6, 7, 8, 9])
     stream = add_noise(original_stream)
+
+    tdnn = TDNN()
+    criterion = nn.MSELoss()
+    optimizer = optim.SGD(tdnn.parameters(), lr=args.nu, momentum=args.momentum)
 
     tdnn_accuracy = []
     tdsnn_accuracy = []
@@ -168,19 +169,22 @@ def main(args):
 if __name__ == '__main__':
     parser = ArgumentParser()
     parser.add_argument('--seed', type=int, default=0)
+    parser.add_argument('--e_size', type=int, default=25)
     parser.add_argument('--noise_level', type=int, default=0)
     parser.add_argument('--no_negative', action='store_true', default=False)
     parser.add_argument('--clean', action='store_true', default=False)
     parser.add_argument('--runtime', type=int, default=500)
+    parser.add_argument('--nu', type=float, default=0.01)
+    parser.add_argument('--momentum', type=float, default=0)
[…]

### 2019-05-05 experiments/htm/config.py
clean up old files

@@ -1,67 +1,0 @@
-MODEL_PARAMS = {
-  "model": "HTMPrediction",
-  "version": 1,
-  "predictAheadTime": None,
-  "modelParams": {
-    "inferenceType": "TemporalMultiStep",
-    "sensorParams": {
-      "verbosity" : 0,
-      "encoders": {
-        "element": {
-          "fieldname": u"element",
-          "name": u"element",
-          "type": "SDRCategoryEncoder",
-          "categoryList": range(50000),
-          "n": 2048,
-          "w": 41
-        }
-      },
-      "sensorAutoReset" : None,
-    },
-      "spEnable": False,
-      "spParams": {
-        "spVerbosity" : 0,
-        "globalInhibition": 1,
-        "columnCount": 2048,
-        "inputWidth": 0,
-        "numActiveColumnsPerInhArea": 40,
-        "seed": 1956,
-        "columnDimensions": 0.5,
-        "synPermConnected": 0.1,
-        "synPermActiveInc": 0.1,
-        "synPermInactiveDec": 0.01,
-        "boostStrength": 0.0
-    },
-    "tmEnable" : True,
-    "tmParams": {
-        "verbosity": 0,
-        "columnCount": 2048,
-        "cellsPerColumn": 32,
-        "inputWidth": 2048,
-        "seed": 1960,
-        "temporalImp": "monitored_tm_py",
-        "newSynapseCount": 32,
-        "maxSynapsesPerSegment": 128,
-        "maxSegmentsPerCell": 128,
-        "initialPerm": 0.21,
-        "connectedPerm": 0.50,
-        "permanenceInc": 0.1,
-        "permanenceDec": 0.1,
-        "predictedSegmentDecrement": 0.02,
-        "globalDecay": 0.0,
-        "maxAge": 0,
-        "minThreshold": 15,
-        "activationThreshold": 15,
-        "outputType": "normal",
-        "pamLength": 1,
-      },
-      "clParams": {
-        "implementation": "cpp",
-        "regionName" : "SDRClassifierRegion",
-        "verbosity" : 0,
-        "alpha": 0.01,
-        "steps": "1",
-      },
-      "trainSPNetOnlyIfRequested": False,
-    },
-}

### 2019-05-05 experiments/htm/htm.py

@@ -1,82 +1,0 @@
-import os
-import dill
-import numpy as np
-from nupic.frameworks.opf.model_factory import ModelFactory
-from nupic.data.inference_shifter import InferenceShifter
-from config import MODEL_PARAMS
-
-dataset_a = [[6, 8, 7, 4, 2, 3, 0],
-             [1, 8, 7, 4, 2, 3, 5],
-             [6, 3, 4, 2, 7, 8, 5],
-             [1, 3, 4, 2, 7, 8, 0],
-             [0, 9, 7, 8, 5, 3, 4, 1],
-             [2, 9, 7, 8, 5, 3, 4, 6],
-             [0, 4, 3, 5, 8, 7, 9, 6],
-             [2, 4, 3, 5, 8, 7, 9, 1]]
-
-dataset_b = [[6, 8, 7, 4, 2, 3, 5],
-             [1, 8, 7, 4, 2, 3, 0],
-             [6, 3, 4, 2, 7, 8, 0],
-             [1, 3, 4, 2, 7, 8, 5],
-             [0, 9, 7, 8, 5, 3, 4, 6],
-             [2, 9, 7, 8, 5, 3, 4, 1],
-             [0, 4, 3, 5, 8, 7, 9, 1],
-             [2, 4, 3, 5, 8, 7, 9, 6]]
-
-seed = 10
-
-seen_noise = set()
-def noise(it):
-    global seen_noise, seed
-    np.random.seed(seed+it)
-    ret = np.random.randint(11,50011)
-    while ret in seen_noise:
-        ret = np.random.randint(11,50011)
-    seen_noise.add(ret)
-    return ret
-
-
-def refresh(seq, tar, it):
-    dataset = dataset_a if it < 10000 else dataset_b
-    chosen = np.random.choice(dataset)
-    target = chosen[1:] + [-1] + [-1]
-    seq.extend(chosen + [noise(it)])
-    tar.extend(target)
-
-
-def get_model():
-    if os.path.isfile('/home/sharathramku/Jupyter/sequence-learning/htm/htm.model'):
-        f = open('htm.model', 'rb')
-        d = dill.load(f)
-        f.close()
-        return d['model']
-    f = open('htm.model', 'wb')
-    htm = ModelFactory.create(MODEL_PARAMS)
-    htm.enableInference({"predictedField": "element"})
-    d = {'model': htm}
-    dill.dump(d, f)
-    f.close()
-    return get_model()
-
-htm = get_model()
-
[…]

### 2019-05-05 results/fetch.sh

@@ -1,5 +1,0 @@
-#!/bin/sh
-scp sharathramku@gypsum:/home/sharathramku/bigdrive/sharath/sequence-learning/experiments/out.zip .
-unzip -o out.zip
-rm out.zip
-python3 results.py

### 2019-05-05 results/results.py

@@ -1,120 +1,0 @@
-
-# coding: utf-8
-
-# In[1]:
-
-
-import os
-import numpy as np
-import matplotlib.pyplot as plt
-
-
-# In[2]:
-
-
-plt.rcParams['figure.figsize'] = [20, 10]
-
-
-# In[3]:
-
-
-def read_td_log_running(fname, minl):
-    file = open(fname, 'r')
-    x = []
-    baseline, tdnn, tdsnn, tdsnnv  = [], [], [], []
-    next(file)
-    for line in file.readlines()[:minl]:
-        it,current,target,random_prediction,tdnn_prediction,tdsnn_prediction,tdsnn_softmax_prediction,tdnn_tl = line.replace('\n','').split(',')
-        x.append(float(it))
-        baseline.append(float(target==random_prediction))
-        tdnn.append(float(target==tdnn_prediction))
-        tdsnn.append(float(target==tdsnn_prediction))
-        tdsnnv.append(float(target==tdsnn_softmax_prediction))
-    return x, baseline, tdnn, tdsnn, tdsnnv
-
-
-# In[4]:
-
-
-def read_lstm_log(fname):
-    file = open(fname, 'r')
-    x = []
-    accuracy = []
-    next(file)
-    for line in file.readlines():
-        it, current, target, prediction, correct = line.replace('\n','').split(',')
-        x.append(float(it))
-        accuracy.append(float(correct))
-    return x, accuracy
-
-
-# In[5]:
-
-
-def moving_average(a, n):
-    moving_average = []
-    for i in range(len(a)):
-        start = max(0, i - n)
-        values = a[start:i+1]
-        moving_average.append(np.sum(values) / float(len(values)))
-    return np.array(moving_average)
-
-
-# In[6]:
-
-
-direc = 'td/'
-td_logs = [direc+i for i in os.listdir(direc) if '.out' in i]
-minl = float('inf')
-for log in td_logs:
-    file = open(log, 'r')
-    minl = min(minl, len(file.readlines())-2)
-
-
-# In[7]:
-
-
-lstm_logs = ['lstm/'+i for i in os.listdir('./lstm/') if '.log' in i]
-
-
-# In[8]:
-
-
[…]

### 2019-05-05 experiments/knn/knn.py
add knn code

@@ -3,12 +3,6 @@ import torch
 import pickle
 import numpy as np
 from argparse import ArgumentParser
-from bindsnet.network import Network
-from bindsnet.network.nodes import RealInput, LIFNodes
-from bindsnet.network.topology import Connection
-from bindsnet.network.monitors import Monitor
-from bindsnet.learning import Hebbian
-
 args = None
 
 
@@ -47,7 +41,7 @@ class Encoder:
             self.encode(i)
 
 
-class KNNClassifier:
+class KNN:
     def __init__(self, k=1):
         self.k = k
         self.data = []
@@ -56,7 +50,7 @@ class KNNClassifier:
         self.data.append((sample, label))
 
     def classify(self, new_sample):
-        distances = [(None, float('inf'))]*self.k
+        distances = [(None, sys.maxsize)]*self.k
         for sample, label in self.data:
             dist = torch.sum(torch.abs(new_sample-sample))
             for i, (_, best_dist) in enumerate(distances):
@@ -71,36 +65,6 @@ class KNNClassifier:
         counts = list(counts.items())
         counts.sort(key=lambda x: x[1])
         return counts[0][0]
-
-
-class Prototype(Network):
-    def __init__(self, encoder, dt: float = 1.0, lag: int = 10, n_neurons: int = 100, time: int = 100, learning: bool = False):
-        super().__init__(dt=dt)
-        self.learning = learning
-        self.n_neurons = n_neurons
-        self.lag = lag
-        self.encoder = encoder
-        self.time = time
-
-        for i in range(lag):
-            self.add_layer(RealInput(n=encoder.e_size,
-                                     traces=True), name=f'input_{i+1}')
-            self.add_layer(LIFNodes(n=self.n_neurons,
-                                    traces=True), name=f'column_{i+1}')
-            self.add_monitor(Monitor(
-                self.layers[f'column_{i+1}'], ['s'], time=self.time), name=f'monitor_{i+1}')
-            w = 0.3*torch.rand(self.encoder.e_size, self.n_neurons)
-            self.add_connection(Connection(source=self.layers[f'input_{i+1}'], target=self.layers[f'column_{i+1}'], w=w), source=f'input_{i+1}', target=f'column_{i+1}')
-
-        for i in range(lag):
-            for j in range(lag):
-                w = torch.zeros(self.n_neurons, self.n_neurons)
[…]

### 2019-05-05 experiments/knn/run.sh

@@ -1,0 +1,2 @@
+#!/bin/sh
+pipenv run python knn.py --seed $1

### 2019-05-05 experiments/knn/submit.sh

@@ -1,0 +1,10 @@
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 0
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 1
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 2
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 3
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 4
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 5
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 6
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 7
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 8
+sbatch -p 1080ti-long --gres=gpu:1 run.sh 9

### 2019-05-05 paper/main.tex
Updates from Overleaf

@@
 \usepackage{graphicx}
+\usepackage{amsmath}
 \usepackage[backend=biber,sorting=none]{biblatex}
@@
 In this study, we explore various neural network models for learning sequences.
-We also compare the robustness of these network models to randomized temporal noise and propose alternative spiking neural architectures.
+We propsed alternative dynamic spiking neural architectures and compare the robustness of these network models to randomized temporal noise.
 \end{abstract}
@@
 
-Neural network models are able to achieve superhuman performance on static tasks through recent break through in deep learning.
+Neural network models are able to achieve superhuman performance on static tasks through recent breakthroughs in deep learning.
 However, the majority of real-world time-series data is often complex and noisy.
@@
     \centering
-    \includegraphics[width=0.7\linewidth]{matrix-distances.png}
+    \includegraphics[width=\linewidth]{../notebooks/matrix-distances.pdf}
     \caption{Heatmap of squared errors between distributed random encodings for the sequence characters, with $-1$ as the separating bit for ease of visualization.}
@@
     \centering
-    \includegraphics[width=0.75\linewidth]{lstm.png}
+    \includegraphics[width=\linewidth]{../diagrams/lstm.png}
     \caption{The network architecture for the LSTM-online model. The LSTM cells maintain an internal hidden state.}
@@
 \cite{waibel1995phoneme} For this task, the TDNN is trained on the last $1000$ characters using a lag of $10$ using backpropagation.
-\cite{rojas1996backpropagation} Again, using the model proposed by Cui et al.
-(2016), the first layer has $250$ input neurons that are fully connected to a hidden layer of $200$ neurons.
-The hidden layers utilize a sigmoid non-linearity and are then fully connected to $25$ output neurons.
+\cite{rojas1996backpropagation} The model has $250$ input neurons that are fully connected to a hidden layer of $200$ neurons.
+The hidden layers utilize a ReLu non-linearity and are fully connected to $25$ output neurons.
+This model proposed by Cui et al.
+have a sigmoid non-linearity in the hidden layer.
+We replaced the non-linearity to allow for conversion into a spiking neural network.
 As with the LSTM model, the output is classified using the nearest neighbor decoder.
@@
     \centering
-    \includegraphics[width=0.75\linewidth]{tdnn.png}
+    \includegraphics[width=\linewidth]{../diagrams/tdnn.png}
     \caption{The network architecture for the TDNN/TDSNN model.}
@@
 A common approach to training spiking neural networks \cite{diehl2015fast} is through the transfer of weights learned through backpropagation on an identical non-spiking neural network and then scaling the weights.
-Using this approach, we can convert the TDNN model trained with a bias on the output layer (due to the lack of negative spikes) to an equivalent spiking network using the approach developed by Diehl et al.
+Using this approach, we can convert the TDNN model trained with backpropagtion into an equivalent spiking network using the approach developed by Diehl et al.
 (2016)
@@
 
+While conversion is one way to train a neural network, it is not energy efficient to perform backpropagation at every time step and then convert.
 We propose a spiking neural network architecture, with $10$ inputs, each fully connected to $1$ of $10$ columns of $100$ spiking neurons.
@@
     \centering
-    \includegraphics[width=0.7\linewidth]{csnn.png}
+    \includegraphics[width=\linewidth]{../diagrams/csnn.png}
     \caption{The network architecture for the CSNN model.}
@@
 \end{figure}
+
+\subsubsection*{Hebbian Learning Rule}
+The Hebbian learning rule for the CSNN model is defined in terms of the spiking activity of its $k$ columns. The weights in a connection from column $i$ to column $j$ is defined as follows:
+
+\begin{equation}
+    \Delta w_{ij} = \eta(s_{i} - \Tilde{s})(s_{j} -  \Tilde{s})
+\end{equation}
+
+where $\eta$ is the learning rate and $\Tilde{s}$ is the mean spiking activity in all the columns, defined as follows:
+
+\begin{equation}
+    \Tilde{s} = \frac{1}{k} \sum_{i = 1}^{k}{s_i}
+    \label{eq:mean_spikes_equation}
+\end{equation}
+
+In equation \ref{eq:mean_spikes_equation}, $s_i$ is the sum of spikes in a column over the duration of the input.
+The weight updates for this model are computed at the end of each input rather than continuously.
 
@@
     \centering
-    \includegraphics[width=0.9\linewidth]{prediction-accuracy.png}
+    \includegraphics[width=0.9\linewidth]{../results/artificial.png}
     \caption{Each of the models were tested on their ability to predict the last element of the sequence.}

### 2019-05-05 experiments/lstm/lstm.py
Update lstm.py

@@ -121,7 +121,7 @@ if __name__ == '__main__':
     parser = ArgumentParser()
     parser.add_argument('--e_size', type=int, default=25)
     parser.add_argument('--h_size', type=int, default=20)
-    parser.add_argument('--window', type=int, default=1000)
+    parser.add_argument('--window', type=int, default=100)
     parser.add_argument('--seed', type=int, default=None)
     parser.add_argument('--noise_level', type=int, default=0)
     parser.add_argument('--clean', action='store_true', default=False)

### 2019-05-05 experiments/lstm/lstm.py
truncate the bptt whoops

@@ -79,10 +79,10 @@ def main():
     optimizer = optim.SGD(model.parameters(), lr=args.nu, momentum=args.momentum)
 
     correct = []
-    prev = None
+    prev = (torch.zeros(1, 1, args.h_size), torch.zeros(1, 1, args.h_size))
     print('it,target,prediction,accuracy')
     for it in range(len(stream) - 2):
-        hidden = prev
+        hidden = (prev[0].detach(), prev[1].detach())
         stored = False
         for jt in range(max(0, it - args.window), it):
             x = stream[jt]

### 2019-05-05 experiments/gru/gru.py
gru implementation lol

@@ -1,0 +1,140 @@
+from argparse import ArgumentParser
+import sys
+import pickle
+import torch
+import torch.nn as nn
+import torch.optim as optim
+import numpy as np
+
+args = None
+
+
+def moving_average(a, n=100):
+    moving = []
+    for i in range(len(a)):
+        start = max(0, i - n)
+        values = a[start:i + 1]
+        moving.append(np.sum(values) / float(len(values)))
+    return np.array(moving)
+
+
+class GRUOnline(nn.Module):
+    def __init__(self):
+        super(GRUOnline, self).__init__()
+        self.inpt = nn.Linear(args.e_size, args.h_size)
+        self.gru = nn.GRU(args.h_size, args.h_size)
+        self.out = nn.Linear(args.h_size, args.e_size)
+
+    def forward(self, x, h=None):
+        x = self.inpt(x.view(1, -1)).unsqueeze(1)
+        x, h = self.gru(x, h)
+        x = self.out(x.squeeze(1))
+        return x, h
+
+
+class Encoder:
+    def __init__(self, e_size=25):
+        self.encodings = {}
+        self.e_size = e_size
+
+    def encode(self, x):
+        if x in self.encodings:
+            return self.encodings[x]
+        self.encodings[x] = 2 * torch.rand(self.e_size) - 1
+        return self.encodings[x]
+
+    def decode(self, v):
+        nearest = None
+        best = float('inf')
+        for x, e in self.encodings.items():
+            dist = (torch.sum((v - e).pow(2))).pow(0.5)
+            if dist < best:
+                best = dist
+                nearest = x
+        return nearest
+
+    def precode(self, stream):
+        for i in stream:
+            self.encode(i)
+
+
+def add_noise(stream):
+    ret = list(stream)
+    subs = [0, 1, 2, 3, 4, 5, 6, 7, 8, 9]
+    for i in range(len(ret)):
+        u = torch.rand(1) * 100
+        if u < args.noise_level:
+            ret[i] = subs[int(torch.randint(0, len(subs), (1,)))]
+    return ret
+
+
+def main():
+    original_stream = pickle.load(open('dataset.pkl', 'rb'))['clean' if args.clean else 'noisy']
+    encoder = Encoder(e_size=args.e_size)
+    encoder.precode([0, 1, 2, 3, 4, 5, 6, 7, 8, 9])
+    stream = add_noise(original_stream)
+
+    model = GRUOnline()
[…]

### 2019-05-05 experiments/gru/run.sh

@@ -1,0 +1,2 @@
+#!/bin/sh
+pipenv run python gru.py --seed $1

### 2019-05-05 experiments/td/run.sh
not a bug but a feature

@@ -1,2 +1,2 @@
 #!/bin/sh
-pipenv run python td.py --seed $1 --no_negative
+pipenv run python td.py --seed $1

### 2019-05-05 experiments/td/run_negative.sh

@@ -1,2 +1,0 @@
-#!/bin/sh
-pipenv run python td.py --seed $1

### 2019-05-05 experiments/td/submit.sh

@@ -8,13 +8,3 @@ sbatch -p 1080ti-long --gres=gpu:1 run.sh 6
 sbatch -p 1080ti-long --gres=gpu:1 run.sh 7
 sbatch -p 1080ti-long --gres=gpu:1 run.sh 8
 sbatch -p 1080ti-long --gres=gpu:1 run.sh 9
-sbatch -p 1080ti-long --gres=gpu:1 run_negative.sh 0
-sbatch -p 1080ti-long --gres=gpu:1 run_negative.sh 1
-sbatch -p 1080ti-long --gres=gpu:1 run_negative.sh 2
-sbatch -p 1080ti-long --gres=gpu:1 run_negative.sh 3
-sbatch -p 1080ti-long --gres=gpu:1 run_negative.sh 4
-sbatch -p 1080ti-long --gres=gpu:1 run_negative.sh 5
-sbatch -p 1080ti-long --gres=gpu:1 run_negative.sh 6
-sbatch -p 1080ti-long --gres=gpu:1 run_negative.sh 7
-sbatch -p 1080ti-long --gres=gpu:1 run_negative.sh 8
-sbatch -p 1080ti-long --gres=gpu:1 run_negative.sh 9

### 2019-05-05 experiments/csnn/run_search.sh
search learning rate again

@@ -1,0 +1,2 @@
+#!/bin/sh
+pipenv run python csnn.py --seed $1 --learning --nu $2

### 2019-05-05 experiments/csnn/search.sh

@@ -1,0 +1,18 @@
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 0 0.1
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 0 0.01
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 0 0.001
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 0 0.0001
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 0 0.00001
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 0 0.000001
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 0 0.0000001
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 0 0.00000001
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 0 0.000000001
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 5 0.1
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 5 0.01
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 5 0.001
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 5 0.0001
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 5 0.00001
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 5 0.000001
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 5 0.0000001
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 5 0.00000001
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 5 0.000000001

### 2019-05-05 experiments/lstm/lstm.py
tweak learning params

@@ -125,8 +125,8 @@ if __name__ == '__main__':
     parser.add_argument('--seed', type=int, default=None)
     parser.add_argument('--noise_level', type=int, default=0)
     parser.add_argument('--clean', action='store_true', default=False)
-    parser.add_argument('--nu', type=float, default=0.05)
-    parser.add_argument('--momentum', type=float, default=0.2)
+    parser.add_argument('--nu', type=float, default=0.01)
+    parser.add_argument('--momentum', type=float, default=0)
     args = parser.parse_args()
 
     print(args)

### 2019-05-05 experiments/td/td.py
tweak td learning params to match curve from numenta paper

@@ -108,6 +108,7 @@ def main():
     stream = add_noise(original_stream)
 
     tdnn = TDNN()
+    tdsnn = convert(tdnn, dataset=None)
     criterion = nn.MSELoss()
     optimizer = optim.SGD(tdnn.parameters(), lr=args.nu, momentum=args.momentum)
 
@@ -116,24 +117,26 @@ def main():
 
     print('it,tdnn_accuracy,tdsnn_accuracy,tdnn_loss,tdsnn_loss,conversion_loss')
     for it in range(11, 20000):
-        dataset = torch.zeros((989, 250))
+        if it > 0 and it % 1000 == 0:
+            dataset = torch.zeros((2989, 250))
+            for _ in range(5):
+                for i in range(max(0, it-3000), it-11):
+                    x = stream[i:i+10]
+                    y = stream[i+10]
 
-        if it > 1000:
-            for i in range(max(0, it-1000), it-11):
-                x = stream[i:i+10]
-                y = stream[i+10]
+                    x_enc = torch.zeros(10*25)
+                    for j, s in enumerate(x):
+                        x_enc[j*25:(j+1)*25] = encoder.encode(s)
+                        dataset[i - max(0, it-3000)][j*25:(j+1)
+                                                     * 25] = x_enc[j*25:(j+1)*25]
+                    y_enc = encoder.encode(y)
 
-                x_enc = torch.zeros(10*25)
-                for j, s in enumerate(x):
-                    x_enc[j*25:(j+1)*25] = encoder.encode(s)
-                    dataset[i - max(0, it-1000)][j*25:(j+1)*25] = x_enc[j*25:(j+1)*25]
-                y_enc = encoder.encode(y)
-
-                y_hat = tdnn(x_enc)
-                optimizer.zero_grad()
-                loss = criterion(y_hat, y_enc)
-                loss.backward()
-                optimizer.step()
+                    y_hat = tdnn(x_enc)
+                    optimizer.zero_grad()
+                    loss = criterion(y_hat, y_enc)
+                    loss.backward()
+                    optimizer.step()
+            tdsnn = convert(tdnn, dataset[:100])
 
         if original_stream[it+2] > 10 or original_stream[it+2] == -1:
             x = stream[it-9:it+1]
@@ -147,8 +150,7 @@ def main():
             tdnn_output = tdnn(x_enc)
[…]

### 2019-05-06 experiments/csnn/search.sh
Update search.sh
refine search

@@ -1,18 +1,20 @@
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 0 0.1
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 0 0.01
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 0 0.001
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 0 0.0001
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 0 0.00001
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 0 0.000001
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 0 0.0000001
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 0 0.00000001
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 0 0.000000001
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 5 0.1
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 5 0.01
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 5 0.001
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 5 0.0001
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 5 0.00001
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 5 0.000001
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 5 0.0000001
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 5 0.00000001
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 5 0.000000001
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 1 0.010
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 1 0.009
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 1 0.008
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 1 0.007
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 1 0.006
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 1 0.005
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 1 0.004
[…]

### 2019-05-06 paper/main.tex
Updates from Overleaf

@@
 \usepackage[backend=biber,sorting=none]{biblatex}
-\usepackage[margin=1.25in]{geometry}
+%\usepackage{geometry}
 \addbibresource{mybib.tex}
@@
 In this study, we explore various neural network models for learning sequences.
-We propsed alternative dynamic spiking neural architectures and compare the robustness of these network models to randomized temporal noise.
+We also propose alternative dynamic spiking neural architectures and compare accuracy and robustness of these network models to randomized temporal noise on a artificial prediction task.
 \end{abstract}
@@
 However, the majority of real-world time-series data is often complex and noisy.
-As a result, we need dynamic models that can adapt to changing data streams to learn and predict in an robust, unsupervised fashion.
+As a result, we need dynamic models that can adapt to changing data streams to learn and predict in an robust, semi-supervised fashion.
 
@@
     \end{tabular}
-    \caption{A sample artificial dataset for this task. The ending character can be predicted by learning the start character and the first character of the shared subsequence.}
+    \caption{A sample artificial dataset for this task.
+The ending character can be predicted by learning the mapping from the start character and the first character of the shared subsequence to the end character.}
     \label{tab:dataset}
@@
     \centering
-    \includegraphics[width=\linewidth]{../notebooks/matrix-distances.pdf}
+    \includegraphics[width=\linewidth]{../notebooks/matrix-distances.png}
     \caption{Heatmap of squared errors between distributed random encodings for the sequence characters, with $-1$ as the separating bit for ease of visualization.}
@@
 (2016) with $25$ input neurons connected to a hidden layer of $20$ LSTM cells and $25$ output neurons.
-The network is trained using backpropagation through time (BPTT) \cite{mozer1995focused} on the last $1000$ seen elements.
+The network is trained using truncated backpropagation through time (TBPTT) \cite{mozer1995focused} on the last $100$ seen elements.
 The output is classified using the nearest neighbor decoder.
+
+\subsubsection*{LSTM Behavior}
+There are many different variants of LSTM implementations.
+In this work, the LSTM cell has a forget gate, but no peephole connections.
+The equations defining the forward pass of the hidden layer in the LSTM model are:
+
+\begin{align*}
+    i_t &= \sigma\left(W_{ii}x_t + W_{hi}h_{t-1} + b_i\right)\\
+    f_t &= \sigma\left(W_{if}x_t + W_{hf}h_{t-1} + b_f\right)\\
+    g_t &= \tanh\left(W_{ig}x_t + W_{hg}h_{t-1} + b_g\right)\\
+    o_t &= \sigma\left(W_{io}x_t + W_{ho}h_{t-1} + b_o\right)\\
+    c_t &= c_{t-1}\ast f_t + i_t \ast g_t\\
+    h_t &= o_t \ast \tanh\left(c_t\right)\\
+\end{align*}
+
+In the above equations, $\sigma$ is the sigmoid activation function, $i_t$ is the input gate, $f_t$ is the forget gate, $g_t$ is the cell gate, $o_t$ is the output gate and the $c_t$ and $h_t$ are the cell and hidden states respectively.
+The $\ast$ operator is the elementwise product operator.
+The biases $\left(b_i, b_f, b_g, b_o\right)$ and weights $\left(W_{ii}, W_{hi}, W_{if}, W_{hf}, W_{ig}, W_{hg},W_{io}, W_{ho}\right)$ are initialized uniformly from $\left[-\frac{1}{k}, \frac{1}{k}\right]$, where $k$ is the number of hidden units.
+These terms are then learned through truncated backpropagation through time (TBPTT) which involves keeping a short history of elements and clipping the gradient updates to the beginning of the history.
+\cite{sutskever2013training}
 
@@
 
-\subsection*{Time-delay spiking neural network (TDSNN)}
+\subsection*{Time-delay spiking neural networks (TDSNN)}
 
@@
 Using this approach, we can convert the TDNN model trained with backpropagtion into an equivalent spiking network using the approach developed by Diehl et al.
-(2016)
-
-\subsubsection*{Readout}
-
+(2016) This method doesn't perform well when the output values are negative.
+To facilitate these negative spikes, the output layer was doubled in size and the negative weight matrix of the original connections was concatentated.
+The same was done for the bias.
+The positive sum of spikes was subracted from the negative sum of spikes and then divided by the runtime to obtain an approximation of the original network's value.
 The drawback of using this method when we need to approximate real-values is the loss of precision based on the duration of the input.
 For this task, we show the input for $500$ simulated milliseconds.
-The summed spikes from the output layer are converted to the $25$ length vector by dividing by the runtime and subtracting $1$.
 As with the other models, the output is classified using the nearest neighbor decoder.
@@
 \subsubsection*{Hebbian Learning Rule}
-The Hebbian learning rule for the CSNN model is defined in terms of the spiking activity of its $k$ columns. The weights in a connection from column $i$ to column $j$ is defined as follows:
+The Hebbian learning rule for the CSNN model is defined in terms of the spiking activity of its $k$ columns.
+The weight change on spike in a connection from column $i$ to column $j$ is defined as follows:
 

### 2019-05-06 experiments/csnn/run.sh
Update run.sh

@@ -1,2 +1,2 @@
 #!/bin/sh
-pipenv run python csnn.py --seed $1 --learning --nu 0.00001
+pipenv run python csnn.py --seed $1 --learning --nu 0.008

### 2019-05-07 experiments/td/run-cl.sh
conversion loss scripts

@@ -1,0 +1,2 @@
+#!/bin/sh
+pipenv run python td.py --seed $1 --runtime $2

### 2019-05-07 experiments/td/submit-cl.sh

@@ -1,0 +1,40 @@
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 25
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 50
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 75
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 100
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 125
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 150
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 175
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 200
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 225
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 250
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 275
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 300
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 325
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 350
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 375
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 400
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 425
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 450
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 475
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 500
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 525
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 550
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 575
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 600
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 625
+sbatch -p 1080ti-long --gres=gpu:1 run-cl.sh 0 650
[…]

### 2019-05-07 paper/main.tex

@@
 \usepackage[backend=biber,sorting=none]{biblatex}
-%\usepackage{geometry}
+\usepackage{geometry}
 \addbibresource{mybib.tex}
@@
 There have been some recent studies comparing various models for time-series prediction tasks \cite{cui2016continuous} on discretized data.
-In this study, we sill replicate their results to establish a baseline and propose unsupervised spiking neural architectures for performing this task.
+In this study, we will replicate their results to establish a baseline and propose unsupervised spiking neural architectures for performing this task.
 Spiking neurons \cite{gerstner2002spiking} are biologically-inspired models of neurons.
@@
     \centering
-    \includegraphics[width=\linewidth]{../notebooks/matrix-distances.png}
+    \includegraphics[width=0.7\linewidth]{../notebooks/matrix-distances.png}
     \caption{Heatmap of squared errors between distributed random encodings for the sequence characters, with $-1$ as the separating bit for ease of visualization.}
@@
 To present each of these discrete categories to the model, we have to encode the categories to a vector representations.
-One possibility is one-hot encoding where the vector is the same size the number of unique characters in the sequence, but this representation scales poorly when the number of unique characters increases.
+One possibility is to one-hot encode each character, but this representation scales poorly when the number of unique characters increases.
 For this reason, the characters are encoded as random vectors with real values in the interval $\left[-1, 1\right]$, similar to distributed representations used in natural language learning.
@@
 The decoder for converting vectors back to character uses a nearest neighbor approach, therefore the precision in the output vector from the model is important as the number of noise characters increases.
-Another possibility to consider for the input encoding would be the sparse distributed categorical encoder utilized by Cui et al.
-(2016) for their hierarchical temporal memory (HTM) model.
 
@@
 (2016) with $25$ input neurons connected to a hidden layer of $20$ LSTM cells and $25$ output neurons.
-The network is trained using truncated backpropagation through time (TBPTT) \cite{mozer1995focused} on the last $100$ seen elements.
+The network is trained using truncated backpropagation through time (TBPTT) \cite{mozer1995focused, sutskever2013training} on the last $100$ seen elements.
 The output is classified using the nearest neighbor decoder.
 
-\subsubsection*{LSTM Behavior}
+\subsubsection*{Long short-term memory (LSTM) Behavior}
 There are many different variants of LSTM implementations.
@@
 The $\ast$ operator is the elementwise product operator.
-The biases $\left(b_i, b_f, b_g, b_o\right)$ and weights $\left(W_{ii}, W_{hi}, W_{if}, W_{hf}, W_{ig}, W_{hg},W_{io}, W_{ho}\right)$ are initialized uniformly from $\left[-\frac{1}{k}, \frac{1}{k}\right]$, where $k$ is the number of hidden units.
-These terms are then learned through truncated backpropagation through time (TBPTT) which involves keeping a short history of elements and clipping the gradient updates to the beginning of the history.
-\cite{sutskever2013training}
+The biases $\left(b_i, b_f, b_g, b_o\right)$ and weights $\left(W_{ii}, W_{hi}, W_{if}, W_{hf}, W_{ig}, W_{hg},W_{io}, W_{ho}\right)$ are initialized uniformly from $\left[-\frac{1}{\sqrt{k}}, \frac{1}{\sqrt{k}}\right]$, where $k$ is the number of hidden units.
+\cite{jozefowicz2015empirical}
 
@@
     \centering
-    \includegraphics[width=\linewidth]{../diagrams/lstm.png}
+    \includegraphics[width=0.9\linewidth]{../diagrams/lstm.png}
     \caption{The network architecture for the LSTM-online model. The LSTM cells maintain an internal hidden state.}
@@
 Time-delay neural networks (TDNN) are feed-forward neural networks trained using a lag on a window of previous data.
-\cite{waibel1995phoneme} For this task, the TDNN is trained on the last $1000$ characters using a lag of $10$ using backpropagation.
+\cite{waibel1995phoneme} For this task, the TDNN is trained on the last $3000$ samples every $1000$ elements with a lag of $10$.
 \cite{rojas1996backpropagation} The model has $250$ input neurons that are fully connected to a hidden layer of $200$ neurons.
-The hidden layers utilize a ReLu non-linearity and are fully connected to $25$ output neurons.
-This model proposed by Cui et al.
-have a sigmoid non-linearity in the hidden layer.
+The hidden layers utilize the ReLU non-linearity and are fully connected to $25$ output neurons.
+The model proposed by Cui et al.
+has a sigmoid non-linearity in the hidden layer.
 We replaced the non-linearity to allow for conversion into a spiking neural network.
@@
     \centering
-    \includegraphics[width=\linewidth]{../diagrams/tdnn.png}
+    \includegraphics[width=0.9\linewidth]{../diagrams/tdnn.png}
     \caption{The network architecture for the TDNN/TDSNN model.}
@@
 
-A common approach to training spiking neural networks \cite{diehl2015fast} is through the transfer of weights learned through backpropagation on an identical non-spiking neural network and then scaling the weights.
-Using this approach, we can convert the TDNN model trained with backpropagtion into an equivalent spiking network using the approach developed by Diehl et al.
-(2016) This method doesn't perform well when the output values are negative.
+A common approach to training spiking neural networks is through the transfer of weights learned through backpropagation on an identical non-spiking neural network and then scaling the weights.
+\cite{diehl2015fast} Using this approach, we can convert the TDNN model trained with backpropagtion into an equivalent spiking network using the approach developed by Diehl et al.
+(2016)
+
+This method works reasonably well when the output values of the network are positive, however the output has values that are negative.
 To facilitate these negative spikes, the output layer was doubled in size and the negative weight matrix of the original connections was concatentated.
 The same was done for the bias.
-The positive sum of spikes was subracted from the negative sum of spikes and then divided by the runtime to obtain an approximation of the original network's value.
+The positive sum of spikes was subtracted from the negative sum of spikes and then divided by the runtime to obtain an approximation of the original network's output.
+
 The drawback of using this method when we need to approximate real-values is the loss of precision based on the duration of the input.
@@
 
-While conversion is one way to train a neural network, it is not energy efficient to perform backpropagation at every time step and then convert.
-We propose a spiking neural network architecture, with $10$ inputs, each fully connected to $1$ of $10$ columns of $100$ spiking neurons.
-Each of the columns has a Hebbian connection to each of the other columns.
+While conversion is one way to train a neural network, it is not energy efficient to perform backpropagation and then convert.
+We propose a spiking neural network architecture, with $10$ inputs, each fully connected to $1$ of $10$ columns of $100$ spiking neurons with randomly initialized weights.
+Each of the columns has a Hebbian connection to each of the other columns initialized with zero weights.
 To map the spikes from this network, we train a K-Nearest Neighbor model using previous spikes and values.
@@
     \centering
-    \includegraphics[width=\linewidth]{../diagrams/csnn.png}
+    \includegraphics[width=0.9\linewidth]{../diagrams/csnn.png}
     \caption{The network architecture for the CSNN model.}
@@
 
+%\subsection*{Leaky Integrate-and-Fire (LIF) Neuron Behavior}
+
+%The Leaky Integrate-and-Fire neuron is used the in the
+
 \section*{Experiments}
@@
 
-%\subsection*{Perturbation}
+\subsection*{Perturbation}
 
-%Another important property of each of these models is the robustness to temporal noise.
+Another important property of each of these models is the robustness to temporal noise.
 We introduce an $\alpha$ parameters which represents the probability that a character is swapped for another character.
@@
 
-%\section*{Conclusion}
+\section*{Conclusion}
 

### 2019-05-07 paper/mybib.tex
Updates from Overleaf

@@
 }
+
+@book{sutskever2013training,
+  title={Training recurrent neural networks},
+  author={Sutskever, Ilya},
+  year={2013},
+  publisher={University of Toronto Toronto, Ontario, Canada}
+}
+
+@inproceedings{jozefowicz2015empirical,
+  title={An empirical exploration of recurrent network architectures},
+  author={Jozefowicz, Rafal and Zaremba, Wojciech and Sutskever, Ilya},
+  booktitle={International Conference on Machine Learning},
+  pages={2342--2350},
+  year={2015}
+}

### 2019-05-08 experiments/td/run-cl-no-neg.sh
td conversion loss without the negative conversion

@@ -1,0 +1,2 @@
+#!/bin/sh
+pipenv run python td.py --seed $1 --runtime $2 --no-negative

### 2019-05-09 paper/main.tex

@@
 \usepackage[english]{babel}
-\usepackage{graphicx}
+\usepackage[draft]{graphicx}
 \usepackage{amsmath}
 \usepackage[backend=biber,sorting=none]{biblatex}
-\usepackage{geometry}
+\usepackage[margin=1.2in]{geometry}
+\usepackage{float}
 \addbibresource{mybib.tex}
@@
 \begin{abstract}
-In this study, we explore various neural network models for learning sequences.
-We also propose alternative dynamic spiking neural architectures and compare accuracy and robustness of these network models to randomized temporal noise on a artificial prediction task.
+In this study, we explore various existing neural network models for learning sequences.
+We also propose alternative dynamic spiking neural architectures and compare accuracy of these network models on an artificial prediction task.
 \end{abstract}
@@
 
-Neural network models are able to achieve superhuman performance on static tasks through recent breakthroughs in deep learning.
+Neural network models are able to achieve superhuman performance on static tasks due to recent breakthroughs in deep learning.
 However, the majority of real-world time-series data is often complex and noisy.
@@
 There have been some recent studies comparing various models for time-series prediction tasks \cite{cui2016continuous} on discretized data.
-In this study, we will replicate their results to establish a baseline and propose unsupervised spiking neural architectures for performing this task.
+In this study, we will replicate their results to establish a baseline and propose semi-surpervised spiking neural architectures for performing this task.
 Spiking neurons \cite{gerstner2002spiking} are biologically-inspired models of neurons.
@@
 Cui et al.
-(2016) propose an artificial dataset of sequences (formed with characters) with overlapping subsequences.
+(2016) propose an artificial dataset of sequences of varying length (formed with characters) with overlapping subsequences.
 A sequence is sampled from the dataset and presented to the model at each time step.
@@
 
-\begin{table}[!h]
+\begin{table}[H]
     \centering
@@
 
-\begin{figure}[!h]
+\subsection*{Input Encoding}
+
+To present each of these discrete categories to the model, we have to encode the categories to a vector representations.
+One possibility is to one-hot encode each character, but this representation scales poorly with the number of unique characters.
+For this reason, the characters are encoded as random vectors with real values in the interval $\left[-1, 1\right]$, similar to distributed representations used in natural language learning.
+\cite{mikolov2013distributed} The euclidean distances between pairs of unique sequence characters using a $25$ length random ending is shown in Figure \ref{fig:encoding-distance}.
+The decoder for converting vectors back to character uses a nearest neighbor approach, therefore the precision in the output vector from the model is important as the number of noise characters increases.
+
+\begin{figure}[H]
     \centering
-    \includegraphics[width=0.7\linewidth]{../notebooks/matrix-distances.png}
+    \includegraphics[width=0.6\linewidth]{../notebooks/matrix-distances.png}
     \caption{Heatmap of squared errors between distributed random encodings for the sequence characters, with $-1$ as the separating bit for ease of visualization.}
@@
 
-\subsection*{Input Encoding}
-
-To present each of these discrete categories to the model, we have to encode the categories to a vector representations.
-One possibility is to one-hot encode each character, but this representation scales poorly when the number of unique characters increases.
-For this reason, the characters are encoded as random vectors with real values in the interval $\left[-1, 1\right]$, similar to distributed representations used in natural language learning.
-\cite{mikolov2013distributed} The euclidean distances between pairs of unique sequence characters using a $25$ length random ending is shown in Figure \ref{fig:encoding-distance}.
-The decoder for converting vectors back to character uses a nearest neighbor approach, therefore the precision in the output vector from the model is important as the number of noise characters increases.
-
-\section*{Models}
+\section*{Supervised Models}
 
@@
 In the above equations, $\sigma$ is the sigmoid activation function, $i_t$ is the input gate, $f_t$ is the forget gate, $g_t$ is the cell gate, $o_t$ is the output gate and the $c_t$ and $h_t$ are the cell and hidden states respectively.
-The $\ast$ operator is the elementwise product operator.
-The biases $\left(b_i, b_f, b_g, b_o\right)$ and weights $\left(W_{ii}, W_{hi}, W_{if}, W_{hf}, W_{ig}, W_{hg},W_{io}, W_{ho}\right)$ are initialized uniformly from $\left[-\frac{1}{\sqrt{k}}, \frac{1}{\sqrt{k}}\right]$, where $k$ is the number of hidden units.
+The $\ast$ operator is the element-wise product operator.
+The biases $\left(b_i, b_f, b_g, b_o\right)$ and weights $\left(W_{ii}, W_{hi}, W_{if}, W_{hf}, W_{ig}, W_{hg},W_{io}, W_{ho}\right)$ are initialized randomly uniformly from $\left[-\frac{1}{\sqrt{k}}, \frac{1}{\sqrt{k}}\right]$, where $k$ is the number of hidden units.
 \cite{jozefowicz2015empirical}
 
-\begin{figure}[!h]
+\begin{figure}[H]
     \centering
@@
 
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=0.9\linewidth]{../diagrams/tdnn.png}
-    \caption{The network architecture for the TDNN/TDSNN model.}
-    \label{fig:lstm-online-model}
-\end{figure}
+The network can be formulated as an equation in terms of the 250 length input vector $x_t$ and the ReLU non-linearity function $R(z)$:
+\begin{equation}
+    \text{TDNN}(x_t) = R\left(x_tW_{ih}^T + b_i\right)W_{ho}^T + b_h
+    \label{eq:tdnn}
+\end{equation}
+In equation \ref{eq:tdnn}, the biases $\left(b_i, b_h\right)$ and the weights $\left(W_{ih}, W_{ho}\right)$ are are initialized randomly uniformly from $\left[-\frac{1}{\sqrt{k_i}}, \frac{1}{\sqrt{k_i}}\right]$, where $k_i$ is the number of input features to the respective layer.
+The weights are then learned through gradient descent.
 
@@
 This method works reasonably well when the output values of the network are positive, however the output has values that are negative.
-To facilitate these negative spikes, the output layer was doubled in size and the negative weight matrix of the original connections was concatentated.
+To facilitate these negative spikes, the output layer was doubled in size and the negative weight matrix of the original connections was concatenated.
 The same was done for the bias.
@@
 For this task, we show the input for $500$ simulated milliseconds.
+The conversion loss, that is, the euclidean distance between the output of the TDNN and the TDSNN is show in Figure \ref{fig:clfig}.
 As with the other models, the output is classified using the nearest neighbor decoder.
 
-%\subsection*{K-Nearest Neighbor (KNN)}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.9\linewidth]{../diagrams/tdnn.png}
+    \caption{The network architecture for the TDNN/TDSNN model.}
+    \label{fig:lstm-online-model}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.5\linewidth]{../results/conversion-loss.png}
+    \caption{Average distance between the output of the TDNN and the TDSNN for different runtimes over the $20,000$ elements in the artificial dataset.}
+    \label{fig:clfig}
+\end{figure}
+
+\section*{Semi-supervised Models}
+
+\subsection*{K-Nearest Neighbor (KNN)}
 
@@
 
-\begin{figure}[!h]
+\begin{figure}[H]
     \centering
@@
 
-The CSNN prediction accuracy dramatically drops after the sequence endings are swapped.
-To improve performance, we can use a window for the data samples in the KNN Classifier.
-Furthermore, the learning rates for the Hebbian updates could be more carefully chosen.
+The KNN (green) reaches perfect accuracy before the dataset is endings are swapped, but fails to relearn the data and only reaches $50\%$ accuracy afterward.
+The TDSNN (orange) is able to match the TDNN (teal) Surprisingly, the CSNN (blue) performance is almost able to match the LSTM (purple) performance.
+However the variance in the CSNN performance is much greater than the LSTM.
 
-\subsection*{Perturbation}
+%\subsection*{Perturbation}
 
-Another important property of each of these models is the robustness to temporal noise.
+%Another important property of each of these models is the robustness to temporal noise.
 We introduce an $\alpha$ parameters which represents the probability that a character is swapped for another character.
@@
 
+We have shown two possible spiking architectures for learning changing patterns in time-series data in a semi-supervised fashion.
+
 \newpage

### 2019-05-09 paper/main.tex
Updates from Overleaf

@@
 \usepackage[backend=biber,sorting=none]{biblatex}
-\usepackage[margin=1.2in]{geometry}
+%\usepackage{geometry}
 \usepackage{float}
@@
 \author{Sharath Ramkumar\\
-Advisor: Dr. Robert Kozma\\University of Massachusetts Amherst\\COMPSCI 496: Independent Study}
+Faculty Advisor: Dr. Robert Kozma\\University of Massachusetts Amherst\\COMPSCI 496: Independent Study}
 \date{}
@@
 As a result, we need dynamic models that can adapt to changing data streams to learn and predict in an robust, semi-supervised fashion.
-
-\section*{Background}
 There have been some recent studies comparing various models for time-series prediction tasks \cite{cui2016continuous} on discretized data.
-In this study, we will replicate their results to establish a baseline and propose semi-surpervised spiking neural architectures for performing this task.
+In this study, we will replicate their results on some of the models to establish a baseline and propose semi-surpervised spiking neural architectures for performing these tasks.
 Spiking neurons \cite{gerstner2002spiking} are biologically-inspired models of neurons.
@@
     \centering
-    \includegraphics[width=0.6\linewidth]{../notebooks/matrix-distances.png}
+    \includegraphics[width=\linewidth]{../notebooks/matrix-distances.png}
     \caption{Heatmap of squared errors between distributed random encodings for the sequence characters, with $-1$ as the separating bit for ease of visualization.}
@@
 
-\begin{align*}
+\begin{align}
     i_t &= \sigma\left(W_{ii}x_t + W_{hi}h_{t-1} + b_i\right)\\
@@
     c_t &= c_{t-1}\ast f_t + i_t \ast g_t\\
-    h_t &= o_t \ast \tanh\left(c_t\right)\\
-\end{align*}
+    h_t &= o_t \ast \tanh\left(c_t\right)
+\end{align}
 
@@
 \cite{rojas1996backpropagation} The model has $250$ input neurons that are fully connected to a hidden layer of $200$ neurons.
-The hidden layers utilize the ReLU non-linearity and are fully connected to $25$ output neurons.
+The hidden layers utilize the ReLU non-linearity and are fully connected to $25$ output neurons for the prediction.
 The model proposed by Cui et al.
@@
 \end{equation}
-In equation \ref{eq:tdnn}, the biases $\left(b_i, b_h\right)$ and the weights $\left(W_{ih}, W_{ho}\right)$ are are initialized randomly uniformly from $\left[-\frac{1}{\sqrt{k_i}}, \frac{1}{\sqrt{k_i}}\right]$, where $k_i$ is the number of input features to the respective layer.
+The biases $\left(b_i, b_h\right)$ and the weights $\left(W_{ih}, W_{ho}\right)$ are initialized randomly uniformly from $\left[-\frac{1}{\sqrt{k_i}}, \frac{1}{\sqrt{k_i}}\right]$, where $k_i$ is the number of input features to the respective layer.
 The weights are then learned through gradient descent.
@@
 
-A common approach to training spiking neural networks is through the transfer of weights learned through backpropagation on an identical non-spiking neural network and then scaling the weights.
-\cite{diehl2015fast} Using this approach, we can convert the TDNN model trained with backpropagtion into an equivalent spiking network using the approach developed by Diehl et al.
-(2016)
+A common approach to training spiking neural networks is through the transfer of weights learned through backpropagation on an identical non-spiking neural network and then scaling the weights through data-based normalization.
+Using this approach, we can convert the TDNN model trained with backpropagtion into an equivalent spiking network.
+\cite{rueckauer2017conversion}
 
-This method works reasonably well when the output values of the network are positive, however the output has values that are negative.
-To facilitate these negative spikes, the output layer was doubled in size and the negative weight matrix of the original connections was concatenated.
+\subsubsection*{Conversion}
+The converted network has neurons that output discrete spikes rather than continuous values.
+Each neuron accumulates voltage $v$ from the previous layer until the voltage reaches a threshold.
+After the voltage surpasses the threshold, the neuron emits a discrete spike to the next layer and the voltage is reset by subtraction of the threshold.
+\cite{diehl2015fast}
+
+The change in the voltages of each of the neurons in the hidden layer $\frac{dV_h}{dt}$ at time $t$ can be written in terms of the input $x_t$, the scale for the connection between the input and hidden layer found through the data-based normalization $\lambda_{ih}$, the transferred connection and bias weights from the TDNN $\left(W_{ih}, b_{i}\right)$, and the neuron spike threshold $\tau$ as:
+
+\begin{equation}
+    \frac{dV^{\left(h\right)}_t}{dt} = \lambda_{ih}\left(W_{ih}^Tx_t + b_i\right) - S^{\left(h\right)}_{t-1}\tau
+\end{equation}
+
+where $S^{\left(h\right)}_{t}$ are the spikes in the hidden layer at time $t$. For each neuron $j$ in the hidden layer, the spike is defined as:
+
+\begin{equation}
+    S^{\left(h,j\right)}_{t} = \begin{cases} 1 & V^{\left(h,j\right)}_{t}\geq \tau \\
+      0 & \text{else.} \\ \end{cases}
+\end{equation}
+
+Similarly the following equation models the change in the voltages of the neurons in the output layer of the TDSNN:
+
+\begin{equation}
+    \frac{dV^{\left(o\right)}_t}{dt} = \lambda_{ho} \left(W_{ho}^TS^{\left(h\right)}_{t} + b_h\right) - S^{\left(o\right)}_{t-1} \tau
+\end{equation}
+
+where $\lambda_{ho}$ is the scale found through the data-based normalization for the connection between the hidden and output layer.
+$S^{\left(o\right)}_{t}$ is the spikes in the output layer at time $t$ which is defined for each neuron $j$ as:
+
+\begin{equation}
+    S^{\left(o,j\right)}_{t} = \begin{cases} 1 & V^{\left(o,j\right)}_{t}\geq \tau \\
+      0 & \text{else.} \\ \end{cases}
+\end{equation}
+
+\subsubsection*{Original Readout}
+The original readout method proposed by Rueckauer et al.
+looks at the voltage of the output layer rather than the spikes.
+This readout method combined with the the subtractive reset mechanism of the spiking neurons in the conversion method perform well on various tasks, \cite{rueckauer2017conversion} but in some cases we may not want to use the voltages.
+One alternative may be to use the average sum of spikes over the total runtime $T$ in the output layer.
+This approximation of the TDNN output values can be written as:
+
+\begin{equation}
+    \text{TDSNN}_{\text{readout1}} = \frac{1}{T} \sum_{t=1}^{T}{S_t^{\left(o\right)}}
+\end{equation}
+
+\subsubsection*{Negative Readout}
+When the output values produced by the TDNN is negative, the average sum of spikes fails to account for the negative output values.
+To account for these negative spikes, the output layer was doubled in size and the negative weight matrix of the original connections was concatenated.
 The same was done for the bias.
-The positive sum of spikes was subtracted from the negative sum of spikes and then divided by the runtime to obtain an approximation of the original network's output.
+The positive sum of spikes was subtracted from the negative sum of spikes and then divided by the runtime $T$ to obtain an approximation of the original network's output.
+For a TDNN that has $l$ neurons in the output layer, the change in voltage for each neuron $j$ in the output layer can be written as:
 
-The drawback of using this method when we need to approximate real-values is the loss of precision based on the duration of the input.
+\begin{equation}
+    \frac{dV^{\left(o\right)}_t}{dt} = 
+    \begin{cases} \lambda_{ho} \left(W_{ho}^TS^{\left(h\right)}_{t} + b_h\right) - S^{\left(o,1:l\right)}_{t-1} \tau & 1 \leq j \leq l  \\
+      \lambda_{ho} \left(-W_{ho}^TS^{\left(h\right)}_{t} - b_h\right) - S^{\left(o,l+1:2l\right)}_{t-1} \tau & l+1 \leq j \leq 2l \\ \end{cases}
+    \label{eq:readout}
+\end{equation}
+
+In Equation \ref{eq:readout}, $W_{ho}$ refers to the original TDNN's weight matrix and $S^{\left(o,j\right)}_{t}$ now has $j \in [1, 2l]$. The new readout is now:
+
+\begin{equation}
+    \text{TDSNN}_{\text{readout2}} = \frac{1}{T} \sum_{t=1}^{T}{\left[S_t^{\left(o,1:l\right)} - S_t^{\left(o,l+1:2l\right)}\right]}
+\end{equation}
+
+\subsubsection*{Conversion Loss}
+The drawback of using spikes instead of voltages to approximate real-values is the loss of precision based on the duration of the input.
 For this task, we show the input for $500$ simulated milliseconds.
-The conversion loss, that is, the euclidean distance between the output of the TDNN and the TDSNN is show in Figure \ref{fig:clfig}.
-As with the other models, the output is classified using the nearest neighbor decoder.
+The conversion loss, defined as the euclidean distance between the output of the TDNN and the TDSNN is shown in Figure \ref{fig:clfig}.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.5\linewidth]{../results/conversion-loss.png}
+    \caption{Average distance between the output of the TDNN and the TDSNN for different runtimes over the $20,000$ elements in the artificial dataset.}
+    \label{fig:clfig}
+\end{figure}
 
@@
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.5\linewidth]{../results/conversion-loss.png}
-    \caption{Average distance between the output of the TDNN and the TDSNN for different runtimes over the $20,000$ elements in the artificial dataset.}
-    \label{fig:clfig}
-\end{figure}
-
 \section*{Semi-supervised Models}
 
-\subsection*{K-Nearest Neighbor (KNN)}
+\subsection*{K-Nearest Neighbors (KNN)}
+
+The K-Nearest Neighbors (KNN) model makes a prediction $\hat{d}_{t+1}$ on an input $x_t$ at time $t$, where $x_t$ is the concatenation of the encodings of the characters $d_i$ for $i \in [t-9, t]$.
+At time $t+1$, the KNN stores the tuple $(x_t, d_{t+1})$.
+To make a prediction, the KNN computes the Euclidean distance from $x_t$ to all other samples.
+The majority vote of the top $k$ samples is taken as the prediction for $d_{t+1}$.
 
@@
 
-While conversion is one way to train a neural network, it is not energy efficient to perform backpropagation and then convert.
-We propose a spiking neural network architecture, with $10$ inputs, each fully connected to $1$ of $10$ columns of $100$ spiking neurons with randomly initialized weights.
-Each of the columns has a Hebbian connection to each of the other columns initialized with zero weights.
-To map the spikes from this network, we train a K-Nearest Neighbor model using previous spikes and values.
+While conversion is one way to train a neural network, it is a supervised method that is not energy efficient on hardware implementations.
+We propose a spiking neural network architecture, with $k$ inputs, each fully connected to $1$ of $k$ columns of $L$ Leaky Integrate-and-Fire (LIF) neurons with randomly initialized weights.
+\cite{gerstner2002spiking} Each neuron in each column has a zero-weight connection to each neuron in each of the other columns.
+The inter-column connections have a Hebbian-inspired update rule.
+To map the spikes from this network, we use the K-Nearest Neighbors model with the sum of spikes of each neuron in each column over the runtime $T$.
 \cite{beliaev2007time} The model diagram is shown in Figure \ref{fig:csnn-network-diagram}.
@@
 The weight updates for this model are computed at the end of each input rather than continuously.
-
-%\subsection*{Leaky Integrate-and-Fire (LIF) Neuron Behavior}
-
-%The Leaky Integrate-and-Fire neuron is used the in the
 

### 2019-05-09 paper/mybib.tex
Updates from Overleaf

@@
 
+@article{rueckauer2017conversion,
+  title={Conversion of continuous-valued deep networks to efficient event-driven networks for image classification},
+  author={Rueckauer, Bodo and Lungu, Iulia-Alexandra and Hu, Yuhuang and Pfeiffer, Michael and Liu, Shih-Chii},
+  journal={Frontiers in neuroscience},
+  volume={11},
+  pages={682},
+  year={2017},
+  publisher={Frontiers}
+}
+
 @inproceedings{diehl2015fast,

### 2019-05-09 experiments/csnn/csnn.py
search

@@ -58,7 +58,7 @@ class KNNClassifier:
     def classify(self, new_sample):
         distances = [(None, float('inf'))]*self.k
         for sample, label in self.data:
-            dist = torch.sum(torch.abs(new_sample-sample))
+            dist = torch.dist(new_sample, sample)
             for i, (_, best_dist) in enumerate(distances):
                 if dist < best_dist:
                     distances[i] = (label, dist)

### 2019-05-09 experiments/csnn/search.sh

@@ -1,20 +1,18 @@
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 1 0.010
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 1 0.009
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 1 0.008
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 1 0.007
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 1 0.006
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 1 0.005
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 1 0.004
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 1 0.003
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 1 0.002
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 1 1
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 1 0.1
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 1 0.01
 sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 1 0.001
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 6 0.010
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 6 0.009
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 6 0.008
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 6 0.007
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 6 0.006
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 6 0.005
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 6 0.004
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 6 0.003
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 6 0.002
-sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 6 0.001
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 1 0.0001
+sbatch -p 1080ti-long --gres=gpu:1 run_search.sh 1 0.00001
[…]

### 2019-05-09 paper/main.tex
Updates from Overleaf

@@
 \usepackage[english]{babel}
-\usepackage[draft]{graphicx}
+\usepackage{graphicx}
 \usepackage{amsmath}
@@
 The $\ast$ operator is the element-wise product operator.
-The biases $\left(b_i, b_f, b_g, b_o\right)$ and weights $\left(W_{ii}, W_{hi}, W_{if}, W_{hf}, W_{ig}, W_{hg},W_{io}, W_{ho}\right)$ are initialized randomly uniformly from $\left[-\frac{1}{\sqrt{k}}, \frac{1}{\sqrt{k}}\right]$, where $k$ is the number of hidden units.
+The biases $\left(b_i, b_f, b_g, b_o\right)$ and weights $\left(W_{ii}, W_{hi}, W_{if}, W_{hf}, W_{ig}, W_{hg},W_{io}, W_{ho}\right)$ are initialized uniformly randomly from $\left[-\frac{1}{\sqrt{k}}, \frac{1}{\sqrt{k}}\right]$, where $k$ is the number of hidden units.
 \cite{jozefowicz2015empirical}
@@
     \includegraphics[width=0.9\linewidth]{../diagrams/lstm.png}
-    \caption{The network architecture for the LSTM-online model. The LSTM cells maintain an internal hidden state.}
+    \caption{The network architecture for the LSTM-online model. The LSTM cells (teal) maintain an internal hidden state.}
     \label{fig:lstm-online-model}
@@
 \end{equation}
-The biases $\left(b_i, b_h\right)$ and the weights $\left(W_{ih}, W_{ho}\right)$ are initialized randomly uniformly from $\left[-\frac{1}{\sqrt{k_i}}, \frac{1}{\sqrt{k_i}}\right]$, where $k_i$ is the number of input features to the respective layer.
+The biases $\left(b_i, b_h\right)$ and the weights $\left(W_{ih}, W_{ho}\right)$ are initialized uniformly randomly from $\left[-\frac{1}{\sqrt{k_i}}, \frac{1}{\sqrt{k_i}}\right]$, where $k_i$ is the number of input features to the respective layer.
 The weights are then learned through gradient descent.
@@
 
-The change in the voltages of each of the neurons in the hidden layer $\frac{dV_h}{dt}$ at time $t$ can be written in terms of the input $x_t$, the scale for the connection between the input and hidden layer found through the data-based normalization $\lambda_{ih}$, the transferred connection and bias weights from the TDNN $\left(W_{ih}, b_{i}\right)$, and the neuron spike threshold $\tau$ as:
+The change in the voltages of each of the neurons in the hidden layer at time $t$ can be written in terms of the input $x_t$, the scale for the connection between the input and hidden layer found through the data-based normalization $\lambda_{ih}$, the transferred connection and bias weights from the TDNN $\left(W_{ih}, b_{i}\right)$, and the neuron spike threshold $\tau$ as:
 
@@
 
-Similarly the following equation models the change in the voltages of the neurons in the output layer of the TDSNN:
-
+Similarly, the following equation models the change in the voltages of the neurons in the output layer of the TDSNN:
 \begin{equation}
@@
 This readout method combined with the the subtractive reset mechanism of the spiking neurons in the conversion method perform well on various tasks, \cite{rueckauer2017conversion} but in some cases we may not want to use the voltages.
-One alternative may be to use the average sum of spikes over the total runtime $T$ in the output layer.
+A more biologically inspired alternative for approximating the output could be the average sum of spikes over the total runtime $T$ in the output layer.
 This approximation of the TDNN output values can be written as:
@@
 The positive sum of spikes was subtracted from the negative sum of spikes and then divided by the runtime $T$ to obtain an approximation of the original network's output.
-For a TDNN that has $l$ neurons in the output layer, the change in voltage for each neuron $j$ in the output layer can be written as:
+
+For a TDNN that has $l$ neurons in the output layer, the change in voltage for each neuron $j$ in the output layer is changed to:
 
@@
     \centering
-    \includegraphics[width=0.5\linewidth]{../results/conversion-loss.png}
+    \includegraphics[width=0.8\linewidth]{../results/conversion-loss.png}
     \caption{Average distance between the output of the TDNN and the TDSNN for different runtimes over the $20,000$ elements in the artificial dataset.}
@@
 
-While conversion is one way to train a neural network, it is a supervised method that is not energy efficient on hardware implementations.
-We propose a spiking neural network architecture, with $k$ inputs, each fully connected to $1$ of $k$ columns of $L$ Leaky Integrate-and-Fire (LIF) neurons with randomly initialized weights.
+While conversion is one way to train a spiking neural network, it is a supervised method that is still not energy efficient on hardware implementations.
+We propose a spiking neural network architecture, with $k$ inputs, each fully connected to $1$ of $k$ columns of $L$ Leaky Integrate-and-Fire (LIF) neurons with weights initialized uniformly randomly from $\left[0, 0.3\right]$.
 \cite{gerstner2002spiking} Each neuron in each column has a zero-weight connection to each neuron in each of the other columns.
@@
 \subsubsection*{Hebbian Learning Rule}
-The Hebbian learning rule for the CSNN model is defined in terms of the spiking activity of its $k$ columns.
-The weight change on spike in a connection from column $i$ to column $j$ is defined as follows:
+The Hebbian learning rule for the CSNN model is defined in terms of the spiking activity of its $k$ columns over the runtime $T$. The sum of spikes in a column $c$ over the runtime is defined as:
 
 \begin{equation}
-    \Delta w_{ij} = \eta(s_{i} - \Tilde{s})(s_{j} -  \Tilde{s})
+    \gamma_c = \sum_{t = 1}^{T}{s_t^{\left(c\right)}}
 \end{equation}
 
-where $\eta$ is the learning rate and $\Tilde{s}$ is the mean spiking activity in all the columns, defined as follows:
+where $s_t^{\left(c\right)}$ is a binary vector that represents the spiking neurons at time $t$ in column $c$. The mean spiking activity for each neuron $\Tilde{s}$ is then defined as:
 
 \begin{equation}
-    \Tilde{s} = \frac{1}{k} \sum_{i = 1}^{k}{s_i}
+    \Tilde{s} = \frac{1}{k} \sum_{c = 1}^{k}{\gamma_c}
     \label{eq:mean_spikes_equation}
@@
 
-In equation \ref{eq:mean_spikes_equation}, $s_i$ is the sum of spikes in a column over the duration of the input.
+The weight change on spike in connections from column $a$ to column $b$ for learning rate $\eta$ is defined as follows:
+
+\begin{equation}
+    \Delta w_{a,b} = \eta * (\gamma_a - \Tilde{s})\otimes(\gamma_b - \Tilde{s})
+\end{equation}
+
 The weight updates for this model are computed at the end of each input rather than continuously.

### 2019-05-09 paper/main.tex
report

@@
 %\usepackage{geometry}
+\usepackage{hyperref}
 \usepackage{float}
@@
 A sample dataset is summarized in Table \ref{tab:dataset}.
+The code and datasets are open-source and available at \href{https://github.com/sharath/sequence-learning}{https://github.com/sharath/sequence-learning}.
 
@@
 
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.7\linewidth]{../notebooks/matrix-distances.png}
+    \caption{Heatmap of squared errors between distributed random encodings for the sequence characters, with $-1$ as the separating bit for ease of visualization.}
+    \label{fig:encoding-distance}
+\end{figure}
+
 \subsection*{Input Encoding}
@@
 The decoder for converting vectors back to character uses a nearest neighbor approach, therefore the precision in the output vector from the model is important as the number of noise characters increases.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{../notebooks/matrix-distances.png}
-    \caption{Heatmap of squared errors between distributed random encodings for the sequence characters, with $-1$ as the separating bit for ease of visualization.}
-    \label{fig:encoding-distance}
-\end{figure}
 
@@
 The weights are then learned through gradient descent.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.9\linewidth]{../diagrams/tdnn.png}
+    \caption{The network architecture for the TDNN/TDSNN model.}
+    \label{fig:lstm-online-model}
+\end{figure}
 
@@
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.9\linewidth]{../diagrams/tdnn.png}
-    \caption{The network architecture for the TDNN/TDSNN model.}
-    \label{fig:lstm-online-model}
-\end{figure}
-
 \section*{Semi-supervised Models}
@@
 
-\section*{Experiments}
+\section*{Results}
 
-\subsection*{Prediction Accuracy}
-
-We tested each of the models (LSTM, TDNN, TDSNN, CSNN) on the discrete sequence learning task.
-The prediction accuracy results are shown in Figure \ref{fig:prediction-accuracy}.
-The prediction accuracy is the percent of correct predictions over a window of the last $100$ sequences.
+\subsection*{Supervised Models}
 
@@
     \centering
-    \includegraphics[width=0.9\linewidth]{../results/artificial.png}
-    \caption{Each of the models were tested on their ability to predict the last element of the sequence.}
-    \label{fig:prediction-accuracy}
+    \includegraphics[width=\linewidth]{../results/artificial-supervised.png}
+    \caption{The TDNN (teal) and TDSNN (orange) models are able to perfectly predict the sequence endings after $4,000$ elements, but their performance drops dramatically after the sequence endings are swapped.
+The LSTM (purple) is able to reach a reasonable performance on this task before the task and the drop after the sequences endings are swapped is only about $30\%$.}
+    \label{fig:prediction-accuracy1}
 \end{figure}
 
-The KNN (green) reaches perfect accuracy before the dataset is endings are swapped, but fails to relearn the data and only reaches $50\%$ accuracy afterward.
-The TDSNN (orange) is able to match the TDNN (teal) Surprisingly, the CSNN (blue) performance is almost able to match the LSTM (purple) performance.
-However the variance in the CSNN performance is much greater than the LSTM.
+\subsection*{Semi-supervised Models}
 
-%\subsection*{Perturbation}
-
-%Another important property of each of these models is the robustness to temporal noise.
-We introduce an $\alpha$ parameters which represents the probability that a character is swapped for another character.
-
-%\subsection*{Continuous Dataset}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\linewidth]{../results/artificial-unsupervised.png}
+    \caption{The KNN (green) reaches perfect accuracy before the dataset is endings are swapped, but fails to relearn the data and only reaches $50\%$ accuracy afterward.
+The CSNN never manages to reach perfect accuracy on the task, but it is able to re-learn the sequence endings after they are swapped after experiencing a drop in performance similar to the LSTM in Figure \ref{fig:prediction-accuracy1}.}
+    \label{fig:prediction-accuracy2}
+\end{figure}
 
@@
 
-We have shown two possible spiking architectures for learning changing patterns in time-series data in a semi-supervised fashion.
+\begin{table}[H]
+    \centering
+    \begin{tabular}{|c|c|} \hline
+        Model & Average Accuracy \\ \hline
+        LSTM  & $0.8049 \pm 0.088$ \\ \hline
+        TDNN  & $0.8112 \pm 0.012$ \\ \hline
+        TDSNN & $0.8097 \pm 0.013$ \\ \hline
+        KNN   & $0.6391 \pm 0.021$ \\ \hline
+        CSNN  & $\textbf{0.8250} \pm 0.119$ \\ \hline
+    \end{tabular}
+    \caption{The average accuracy on the discrete sequence learning task over $10$ randomized runs.}
+    \label{tab:meanaccuracy}
+\end{table}
 
-\newpage
+We have shown two possible spiking architectures for learning changing patterns in time-series data.
+We tested each of the models (LSTM, TDNN, TDSNN, KNN, CSNN) on the discrete sequence learning task.
+The TDSNN (orange) is able to match the TDNN (teal) Surprisingly, the CSNN (blue) performance over $10$ runs has the highest average accuracy over the sequence learning task, but it also has the average standard deviation over the $10$ runs.
+
 \printbibliography[title={References}]
